---
title: "fMRI_Trailer_SNE"
author: "Luis A."
date: "2024-05-07"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Add pairplots. 
# Add combined com hor models. 

# Loading libraries
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
library(car)
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
library(modelsummary)
library(pandoc)
library(tinytable)
library(cowplot)
```


```{r, echo=FALSE}

Individual_comedy_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC_Comedy.csv')

Aggregate_comedy_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Aggregate_Combined_Comedy_filtered.csv')

Individual_horror_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC_Horror.csv')

Aggregate_horror_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Aggregate_Combined_Horror_filtered.csv')

Individual_BothTrailers_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC.csv') %>% mutate(Type = factor(Type, levels = c("Comedy", "Horror")))

Aggregate_BothTrailers_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Aggregate_Combined_filtered.csv') %>% mutate(Type = factor(Type, levels = c("comedy", "horror")))

```

```{r, echo=FALSE}
# Association between first month and total gross/theaters.

#plot1 <- ggplot(Aggregate_BothTrailers_df, aes(x = (GrossOverTheaters_M1), y = (GrossOverTheaters_Total), color=Type)) +
#  labs(y = "Cummulative GT Total", x = "Cummulative GT M1") + 
#  geom_point() +
#  geom_smooth(method = "lm") +
#  stat_cor() +
#  geom_text(aes(label = Trailer), vjust = 2)

#plot1

#plot2 <- ggplot(Aggregate_BothTrailers_df, aes(x = (GT_AVG_M1), y = (GT_AVG_Total), color=Type)) +
#  labs(y = "AVG GT Per Week (Total)", x = "AVG GT Per Week (M1)") + 
#  geom_point() +
#  geom_smooth(method = "lm") +
#  stat_cor() +
# geom_text(aes(label = Trailer), vjust = 2)

#plot2

#plot_grid(plot1, plot2, )



```

```{r}
# DVs pairplot.

#Gross_W1 <- Aggregate_BothTrailers_df$DG_WK1
#Gross_W2 <- Aggregate_BothTrailers_df$DG_WK2
#Gross_W3 <- Aggregate_BothTrailers_df$DG_WK3
#Gross_M1 <- Aggregate_BothTrailers_df$Gross_US_M1
#Gross_Total <- Aggregate_BothTrailers_df$Gross_Total_US

#DV_df <- tibble(Gross_W1, Gross_W2, Gross_W3, Gross_M1, Gross_Total) 

ggpairs(Aggregate_BothTrailers_df[, c("Type", "Gross_US_W1_num", "Gross_US_W2_num", "Gross_US_W3_num", "Gross_US_M1", "Gross_Total_US")], columns = 2:ncol(Aggregate_BothTrailers_df[, c("Type", "Gross_US_W1_num", "Gross_US_W2_num", "Gross_US_W3_num","Gross_US_M1", "Gross_Total_US")]), 
        aes(color = Type)) 

```

```{r}
ggpairs(Aggregate_BothTrailers_df[, c("Type", "DG_WK1", "DG_WK2", "DG_WK3", "DG_WK4", "Gross_Total_US")], columns = 2:ncol(Aggregate_BothTrailers_df[, c("Type", "DG_WK1", "DG_WK2", "DG_WK3", "DG_WK4", "Gross_Total_US")]), 
        aes(color = Type)) 
```


# Invididual Choice Comedy (IndCom) Trailers.
## IndCom: Sequence model.
```{r, echo=FALSE}
# Create affect only model. 
IndCom_Affect <- lmer(scale(W_score_scaled) ~ 
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        (1|Participant) + (1|Trailer), data = Individual_comedy_df)

# Create neuro sequence only model.
IndCom_SeqNeuro <- lmer(scale(W_score_scaled) ~ 
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), data = Individual_comedy_df)

# Create affect and neuro sequence model.
IndCom_Affect_and_SeqNeuro <- lmer(scale(W_score_scaled) ~ 
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), data = Individual_comedy_df)

# Create list with all models.
IndCom_Seq_list <- list(
  "Affect" = IndCom_Affect, 
  "Neuro seq" = IndCom_SeqNeuro, 
  "Affect & Neuro seq" = IndCom_Affect_and_SeqNeuro)

# Make table with all models. 
IndCom_Seq_models <- modelsummary(IndCom_Seq_list, stars=TRUE, 
                           statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #output = "Seq_models_C.docx",
                           output = "html",
                           #output="dataframe",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)",
                           title = 'Individual Choice (Comedy): Sequence Models.') #%>% select(-part, -statistic)

IndCom_Seq_models
```

```{r, echo=FALSE}
W_score_C <- Individual_comedy_df$W_score_scaled
PA_C <- Individual_comedy_df$Pos_arousal_scaled
NA_C <- Individual_comedy_df$Neg_arousal_scaled
NAcc_seg2 <- Individual_comedy_df$NAcc_seg2
AIns_seg3 <- Individual_comedy_df$AIns_seg3
MPFC_seg5 <- Individual_comedy_df$MPFC_seg5

IndCom_Seq_df <- tibble(W_score_C, PA_C, NA_C, NAcc_seg2, AIns_seg3, MPFC_seg5) 
ggpairs(IndCom_Seq_df)
```


## IndCom: Modal Peak (MP) Model.
```{r, echo=FALSE}
# Create neuro MP only model.
IndCom_MP <- lmer(scale(W_score_scaled) ~ 
                        scale(NAcc_avg_peak_yes_pos) + 
                        scale(AIns_avg_peak_yes_pos) + 
                        scale(MPFC_avg_peak_yes_pos) +
                        (1|Participant) + (1|Trailer), data = Individual_comedy_df)

# Create affect and neuro MP model.
IndCom_Affect_and_MP <- lmer(scale(W_score_scaled) ~ 
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_avg_peak_yes_pos) + 
                        scale(AIns_avg_peak_yes_pos) + 
                        scale(MPFC_avg_peak_yes_pos) +
                        (1|Participant) + (1|Trailer), data = Individual_comedy_df)

# Create list with all models.
IndCom_MP_list <- list(
  "Affect" = IndCom_Affect, 
  "Neuro MP" = IndCom_MP, 
  "Affect & Neuro MP" = IndCom_Affect_and_MP)

# Make table with all models. 
IndCom_MP <- modelsummary(IndCom_MP_list, stars=TRUE, 
                           statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           output = "html",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)",
                           title = 'Individual Choice (Comedy): Modal Peaks Models.') #%>% select(-part, -statistic)

IndCom_MP
```

```{r, echo=FALSE}
W_score <- Individual_comedy_df$W_score_scaled
PA <- Individual_comedy_df$Pos_arousal_scaled
NA_ <- Individual_comedy_df$Neg_arousal_scaled
NAcc_MP <- Individual_comedy_df$NAcc_avg_peak_yes_pos
AIns_MP <- Individual_comedy_df$AIns_avg_peak_yes_pos
MPFC_MP <- Individual_comedy_df$MPFC_avg_peak_yes_pos

IndCom_MP_df <- tibble(W_score, PA, NA_, NAcc_MP, AIns_MP, MPFC_MP) 
ggpairs(IndCom_MP_df)

```


# Aggregate Results Comedy Trailers.
```{r, echo=FALSE}
# Create aggregate base and affect models for comedy trailers.

# Create base aggregate model for first month gross (raw).
AggCom_G_raw <- lm(scale(GrossM1) ~ scale(TheatersM1)
            , data = Aggregate_comedy_df)

# Create base aggregate model for first month gross (log).
AggCom_G_log <- lm(log(GrossM1) ~ scale(TheatersM1)
            , data = Aggregate_comedy_df)

# Create base aggregate model for first month gross (log).
AggCom_G_rank <- lm(rank(GrossM1) ~ scale(TheatersM1)
            , data = Aggregate_comedy_df)

# Create affect aggregate model for first month gross (raw).
AggCom_Affect_G_raw <- lm(scale(GrossM1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_comedy_df)

# Create affect aggregate model for first month gross (log).
AggCom_Affect_G_log <- lm(log(Gross_US_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_comedy_df)

# Create affect aggregate model for first month gross (rank).
AggCom_Affect_G_rank <- lm(rank(Gross_US_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_comedy_df)

# Create affect aggregate model for first month gross (rank).
AggCom_Choice_G_rank <- lm(rank(Gross_US_M1) ~ 
        + scale(W_score_scaled) 
            , data = Aggregate_comedy_df)

# Create aggregate model for first month gross (raw) controlling for number of theaters.
AggCom_GT_raw <- lm(scale(GT_AVG_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_comedy_df)

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggCom_GT_log <- lm(log(Gross_US_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_comedy_df)

# Create aggregate model for first month gross (log) controlling for number of theaters.
ChoiceCom_GT_log <- lm(log(Gross_US_M1) ~ 
         + scale(W_score_scaled) 
            , data = Aggregate_comedy_df)

# Create aggregate model for first month gross (rank) controlling for number of theaters.
AggCom_GT_rank <- lm(rank(GT_AVG_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_comedy_df )

```

## AggCom: Seq Models.
```{r, echo=FALSE}

# Create aggregate model for comedy neuro seq (raw) controlling for number of theaters.
AggCom_Seq_GT_rank <- lm(rank(Gross_US_M1) ~ 
          + scale(NAcc_seg1)  
          + scale(AIns_seg3) 
          + scale(MPFC_seg5) 
            , data = Aggregate_comedy_df)

AggCom_AffectNeuroSeq_GT_rank <- lm(rank(Gross_US_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
          + scale(NAcc_seg1)  
          + scale(AIns_seg3) 
          + scale(MPFC_seg5) 
            , data = Aggregate_comedy_df)

# Create aggregate model for comedy neuro seq (raw) and affect controlling for number of theaters.
AggCom_ChoiceSeq_GT_rank <- lm(rank(Gross_US_M1) ~ 
         + scale(W_score_scaled) 
          + scale(NAcc_seg1)  
          + scale(AIns_seg3) 
          + scale(MPFC_seg5) 
            , data = Aggregate_comedy_df)

AggCom_Seq_list = list(
  "Affect GM1" = AggCom_Affect_G_rank,
  "Choice GM1" = AggCom_Choice_G_rank,
  "Neuro Seq GM1" = AggCom_Seq_GT_rank,
  "Affect Neuro Seq GM1" = AggCom_AffectNeuroSeq_GT_rank,
  "Choice Neuro Seq GM1" = AggCom_ChoiceSeq_GT_rank)

AggCom_Seq_models <- modelsummary(AggCom_Seq_list, stars=TRUE, 
                               statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #output="AggRank_seq_comedy_models.docx", 
                               #output="dataframe",
                               output="html",
                               gof_omit = "F|RMSE|Log") #%>% select(-part, -statistic)
AggCom_Seq_models
```

```{r}
ggplot(Aggregate_comedy_df, aes(x = (NAcc_seg1), y = rank(Gross_US_M1))) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor() +
  geom_text(aes(label = Trailer), vjust = 2)
```

```{r}
GT_M1 <- rank(Aggregate_comedy_df$Gross_US_M1)
W_score_C <- Aggregate_comedy_df$W_score_scaled
PA_C <- Aggregate_comedy_df$Pos_arousal_scaled
NA_C <- Aggregate_comedy_df$Neg_arousal_scaled
NAcc_seg1 <- Aggregate_comedy_df$NAcc_seg1
AIns_seg3 <- Aggregate_comedy_df$AIns_seg3
MPFC_seg5 <- Aggregate_comedy_df$MPFC_seg5

AggCom_Seq_df <- tibble(GT_M1, W_score_C, PA_C, NA_C, NAcc_seg1, AIns_seg3, MPFC_seg5) 
ggpairs(AggCom_Seq_df)
```


## AggCom: Modal Peak (MP) Models.
```{r, echo=FALSE}

# Create aggregate model for comedy neuro MP (log) controlling for number of theaters.
AggCom_MP_GT_rank <- lm(rank(Gross_US_M1) ~ 
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2)
         + scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_comedy_df)

AggCom_MPAffect_GT_rank <- lm(rank(Gross_US_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2)
         + scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_comedy_df)

# Create aggregate model for comedy neuro MP (log) and affect controlling for number of theaters.
AggCom_FullMPA_GT_rank <- lm(rank(Gross_US_M1) ~ 
         + scale(W_score_scaled) 
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2)
         + scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_comedy_df)

AggCom_MP_list = list(
  "Affect GM1" = AggCom_Affect_G_rank,
  "Choice GM1" = AggCom_Choice_G_rank,
  "Neuro MP GM1" = AggCom_MP_GT_rank,
  "Affect Neuro MP GM1" = AggCom_MPAffect_GT_rank,
  "Choice Neuro MP GM1" = AggCom_FullMPA_GT_rank)

AggCom_MP_models <- modelsummary(AggCom_MP_list, stars=TRUE, 
                               statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #output="AggRank_seq_comedy_models.docx", 
                               #output="dataframe",
                               output="html",
                               gof_omit = "F|RMSE|Log") #%>% select(-part, -statistic)
AggCom_MP_models

```

```{r}

#AllSubs_NeuralActivation <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Aggregate_Combined_Comedy_clean.csv') #%>%
  #filter(Trailer!="uc2")
  #filter(Trailer!="uc3", Trailer!="rc11", Trailer!="rc7")

#ggplot(Aggregate_comedy_df, aes(x = (NAcc_avg_peak_yes_pos), y = log(GrossTheatersM1))) +
# labs(y = "First month Gross/Theaters", x = "NAcc Modal Peak") + 
#  ggtitle("Neuroforecasting Comedy Trailers NAcc Modal Peak") + 
#  geom_point() +
#  geom_smooth(method = "lm") +
#  stat_cor() +
#  geom_text(aes(label = Trailer), vjust = 2)

GT_M1 <- rank(Aggregate_comedy_df$Gross_US_M1)
W_C <- Aggregate_comedy_df$W_score_scaled
PA_C <- Aggregate_comedy_df$Pos_arousal_scaled
NA_C <- Aggregate_comedy_df$Neg_arousal_scaled
NAcc_MP <- Aggregate_comedy_df$NAcc_avg_peak_yes_pos2
AIns_MP <- Aggregate_comedy_df$AIns_avg_peak_yes_pos2
MPFC_MP <- Aggregate_comedy_df$MPFC_avg_peak_yes_pos2

AggCom_MP_df <- tibble(GT_M1, W_C, PA_C, NA_C, NAcc_MP, AIns_MP, MPFC_MP) 
ggpairs(AggCom_MP_df)
```

# Individual Results Horror Trailers. 
## IndHor: Sequence models.
```{r, echo=FALSE}
# Create affect only model. 
IndHor_Affect <- lmer(scale(W_score_scaled) ~ 
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        (1|Participant) + (1|Trailer), data = Individual_horror_df)

# Create neuro sequence only model.
IndHor_SeqNeuro <- lmer(scale(W_score_scaled) ~ 
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), data = Individual_horror_df)

# Create affect and neuro sequence model.
IndHor_Affect_and_SeqNeuro <- lmer(scale(W_score_scaled) ~ 
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), data = Individual_horror_df)

# Create list with all models.
IndHor_Seq_list <- list(
  "Affect" = IndHor_Affect, 
  "Neuro seq" = IndHor_SeqNeuro, 
  "Affect & Neuro seq" = IndHor_Affect_and_SeqNeuro)

# Make table with all models. 
IndHor_Seq_models <- modelsummary(IndHor_Seq_list, stars=TRUE, 
                           statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           output = "html",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)")
                           #title = 'Individual Choice (Horror): Sequence Models.') #%>% select(-part, -statistic)

IndHor_Seq_models
```

```{r, echo=FALSE}
W_score_H <- Individual_horror_df$W_score_scaled
PA_H <- Individual_horror_df$Pos_arousal_scaled
NA_H <- Individual_horror_df$Neg_arousal_scaled
NAcc_seg2 <- Individual_horror_df$NAcc_seg2
AIns_seg3 <- Individual_horror_df$AIns_seg3
MPFC_seg5 <- Individual_horror_df$MPFC_seg5

IndHor_MP_df <- tibble(W_score_H, PA_H, NA_H, NAcc_seg2, AIns_seg3, MPFC_seg5) 
ggpairs(IndHor_MP_df)
```


## IndHor: Modal Peak (MP) Model.
```{r, echo=FALSE}
# Create neuro MP only model.
IndHor_MP <- lmer(scale(W_score_scaled) ~ 
                        scale(NAcc_avg_peak_yes_pos2) + 
                        scale(AIns_avg_peak_yes_pos2) + 
                        scale(MPFC_avg_peak_yes_pos2) +
                        (1|Participant) + (1|Trailer), data = Individual_horror_df)

# Create affect and neuro MP model.
IndHor_Affect_and_MP <- lmer(scale(W_score_scaled) ~ 
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_avg_peak_yes_pos2) + 
                        scale(AIns_avg_peak_yes_pos2) + 
                        scale(MPFC_avg_peak_yes_pos2) +
                        (1|Participant) + (1|Trailer), data = Individual_horror_df)

# Create list with all models.
IndHor_MP_list <- list(
  "Affect" = IndHor_Affect, 
  "Neuro MP" = IndHor_MP, 
  "Affect & Neuro MP" = IndHor_Affect_and_MP)

# Make table with all models. 
IndHor_MP <- modelsummary(IndHor_MP_list, stars=TRUE, 
                           statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           output = "html",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)")
                           #title = 'Individual Choice (Comedy): Modal Peaks Models.') #%>% select(-part, -statistic)

IndHor_MP
```

```{r, echo=FALSE}
W_score_H <- Individual_horror_df$W_score_scaled
PA_H <- Individual_horror_df$Pos_arousal_scaled
NA_H <- Individual_horror_df$Neg_arousal_scaled
NAcc_MP <- Individual_horror_df$NAcc_avg_peak_yes_pos2
AIns_MP <- Individual_horror_df$AIns_avg_peak_yes_pos2
MPFC_MP <- Individual_horror_df$MPFC_avg_peak_yes_pos2

IndHor_MP_df <- tibble(W_score_H, PA_H, NA_H, NAcc_MP, AIns_MP, MPFC_MP) 
ggpairs(IndHor_MP_df)
```

# Aggregate Results Horror Trailers. 
```{r, echo=FALSE}
# Create base aggregate model for first month gross (log).
AggHor_G_log <- lm(log(GrossM1) ~ scale(TheatersM1)
            , data = Aggregate_horror_df)

# Create affect aggregate model for first month gross (log).
AggHor_Affect_G_log <- lm(log(GrossM1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_horror_df)

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggHor_GT_log <- lm(log(GT_AVG_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_horror_df)

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggHor_Choice_GT_log <- lm(log(GT_AVG_M1) ~ 
         + scale(W_score_scaled) 
            , data = Aggregate_horror_df)



# Create affect aggregate model for first month gross (log).
AggHor_Affect_G_rank <- lm(rank(GrossM1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = Aggregate_horror_df)

# Create affect aggregate model for first month gross (log).
AggHor_Choice_G_rank <- lm(rank(GrossM1) ~ 
            + scale(W_score_scaled) 
            , data = Aggregate_horror_df)

```

## AggHor: Seq Models.
```{r, echo=FALSE}

# Create aggregate model for comedy neuro seq (log) controlling for number of theaters.
AggHor_Seq_GT_rank <- lm(rank(GrossM1) ~ 
          + scale(NAcc_seg1)  
          + scale(AIns_seg3) 
          + scale(MPFC_seg5) 
            , data = Aggregate_horror_df)

AggHor_SeqAffect_GT_rank <- lm(rank(GrossM1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
          + scale(NAcc_seg1)  
          + scale(AIns_seg3) 
          + scale(MPFC_seg5) 
            , data = Aggregate_horror_df)

# Create aggregate model for comedy neuro seq (log) and affect controlling for number of theaters.
AggHor_SeqChoice_GT_rank <- lm(rank(GrossM1) ~ 
         + scale(W_score_scaled) 
          + scale(NAcc_seg1)  
          + scale(AIns_seg3) 
          + scale(MPFC_seg5) 
            , data = Aggregate_horror_df)

AggHor_Seq_list = list(
  "Affect GT" = AggHor_Affect_G_rank, 
  "Choice GT" = AggHor_Choice_G_rank,
  "Neuro Seq GT" = AggHor_Seq_GT_rank,
  "Affect Neuro Seq GT" = AggHor_SeqAffect_GT_rank,
  "Choice Neuro Seq GT" = AggHor_SeqChoice_GT_rank)

AggHor_Seq_models <- modelsummary(AggHor_Seq_list, stars=TRUE, 
                               statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #output="dataframe",
                               output="html",
                               gof_omit = "F|RMSE|Log") #%>% select(-part, -statistic)
AggHor_Seq_models

```

```{r, echo=FALSE}
GrossM1_rank <- rank(Aggregate_horror_df$GrossM1)
W_score_H <- Aggregate_horror_df$W_score_scaled
PA_H <- Aggregate_horror_df$Pos_arousal_scaled
NA_H <- Aggregate_horror_df$Neg_arousal_scaled
NAcc_seg1 <- Aggregate_horror_df$NAcc_seg1
AIns_seg3 <- Aggregate_horror_df$AIns_seg3
MPFC_seg5 <- Aggregate_horror_df$MPFC_seg5

AggHor_Seq_df <- tibble(GrossM1_rank, W_score_H, PA_H, NA_H, NAcc_seg1, AIns_seg3, MPFC_seg5) 
ggpairs(AggHor_Seq_df)
```


## AggHor: Modal Peak (MP) Models.
```{r, echo=FALSE}

# Create aggregate model for horror neuro MP (raw) controlling for number of theaters.
AggHor_MP_GT_rank <-  lm(rank(GrossM1) ~ 
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2)
         + scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_horror_df)

AggHor_MPAffect_GT_rank <-  lm(rank(GrossM1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2)
         + scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_horror_df)

# Create aggregate model for horror neuro MP (raw) and affect controlling for number of theaters.
AggHor_ChoiceMP_GT_rank <-  lm(rank(GrossM1) ~ 
         + scale(W_score_scaled)
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2)
         + scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_horror_df)

AggHor_MP_list = list(
  "Affect GT" = AggHor_Affect_G_rank, 
  "Choice GT" = AggHor_Choice_G_rank,
  "Neuro MP GT" = AggHor_MP_GT_rank,
  "Affect Neuro MP GT" = AggHor_MPAffect_GT_rank,
  "Choice Neuro MP GT" = AggHor_ChoiceMP_GT_rank)

AggHor_MP_models <- modelsummary(AggHor_MP_list, stars=TRUE, 
                               statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #output="AggRank_seq_comedy_models.docx", 
                               #output="dataframe",
                               output="html",
                               gof_omit = "F|RMSE|Log") #%>% select(-part, -statistic)
AggHor_MP_models

```

```{r, echo=FALSE}
GT_M1 <- log(Aggregate_horror_df$GT_AVG_M1)
W_score_H <- Aggregate_horror_df$W_score_scaled
PA_H <- Aggregate_horror_df$Pos_arousal_scaled
NA_H <- Aggregate_horror_df$Neg_arousal_scaled
NAcc_MP <- Aggregate_horror_df$NAcc_avg_peak_yes_pos2
AIns_MP <- Aggregate_horror_df$AIns_avg_peak_yes_pos2
MPFC_MP <- Aggregate_horror_df$MPFC_avg_peak_yes_pos2

AggHor_MP_df <- tibble(GT_M1, W_score_H, PA_H, NA_H, NAcc_MP, AIns_MP, MPFC_MP) 
ggpairs(AggHor_MP_df)
```

# Invididual Choice Both Trailers.
## IndBoth: Sequence models.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

Individual_BothTrailers_df <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC.csv') %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy")))

contrasts(Individual_BothTrailers_df$Type) <- rbind(-1, 1)
colnames(contrasts(Individual_BothTrailers_df$Type)) <- levels(Individual_BothTrailers_df$Type)[2]

# Create affect only model. 
IndBoth_Affect <- lmer(scale(W_score_scaled) ~ 
                        Type +
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create neuro sequence only model.
IndBoth_SeqNeuro <- lmer(scale(W_score_scaled) ~
                        Type +   
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        Type:scale(NAcc_seg2) + 
                        Type:scale(AIns_seg3) + 
                        Type:scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and neuro sequence model.
IndBoth_Affect_and_SeqNeuro <- lmer(scale(W_score_scaled) ~
                        Type +              
                        scale(Pos_arousal_scaled) +
                        scale(Neg_arousal_scaled) +
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_seg2) +
                        Type:scale(AIns_seg3) +
                        Type*scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

#summary(IndBoth_Affect_and_SeqNeuro) 
# Create list with all models.
IndBoth_Seq_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro seq" = IndBoth_SeqNeuro, 
  "Affect & Neuro seq" = IndBoth_Affect_and_SeqNeuro)

# Make table with all models. 
IndBoth_Seq_models <- modelsummary(IndBoth_Seq_list, stars=TRUE, 
                           statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           output = "html",
                           #output = "dataframe",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") #%>% select(-part, -statistic)


print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_Seq_models
```

```{r, echo=FALSE}
#ggpairs(IndBoth_Affect_and_SeqNeuro[, c("Type", "W_score_scaled", "Pos_arousal_scaled", "Neg_arousal_scaled", "NAcc_seg2", "AIns_seg3", "MPFC_seg5")], columns = 2:ncol(IndBoth_Affect_and_SeqNeuro[, c("Type", "W_score_scaled", "Pos_arousal_scaled", "Neg_arousal_scaled", "NAcc_seg2", "AIns_seg3", "MPFC_seg5")]), 
#        aes(color = Type)) 

```


## IndBoth: MP models.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Create neuro sequence only model.
IndBoth_MPNeuro <- lmer(scale(W_score_scaled) ~
                        Type +   
                        scale(NAcc_avg_peak_yes_pos2) +
                        scale(AIns_avg_peak_yes_pos2) +
                        scale(MPFC_avg_peak_yes_pos2) +
                        Type:scale(NAcc_avg_peak_yes_pos2) + 
                        Type:scale(AIns_avg_peak_yes_pos2) + 
                        Type:scale(MPFC_avg_peak_yes_pos2) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 
                        #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

# Create affect and neuro sequence model.
IndBoth_Affect_and_MPNeuro <- lmer(scale(W_score_scaled) ~
                        Type +              
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_avg_peak_yes_pos2) +
                        scale(AIns_avg_peak_yes_pos2) +
                        scale(MPFC_avg_peak_yes_pos2) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_avg_peak_yes_pos2) + 
                        Type:scale(AIns_avg_peak_yes_pos2) + 
                        Type:scale(MPFC_avg_peak_yes_pos2) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df)
                        #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

#, data = Aggregate_BothTrailers_df %>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

# Create list with all models.
IndBoth_MP_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro seq" = IndBoth_MPNeuro, 
  "Affect & Neuro seq" = IndBoth_Affect_and_MPNeuro)

# Make table with all models. 
IndBoth_MP_models <- modelsummary(IndBoth_MP_list, stars=TRUE, 
                           statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           output = "html",
                           #output = "dataframe",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") #%>% select(-part, -statistic)

print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_MP_models
```

# Aggregate Results Both Trailers. 
## AggBoth: Seq Models.
```{r, echo=FALSE}
Aggregate_BothTrailers_df <- mutate(Aggregate_BothTrailers_df, Type = factor(Type, levels = c("horror", "comedy")))
contrasts(Aggregate_BothTrailers_df$Type) <- rbind(-1, 1)
colnames(contrasts(Aggregate_BothTrailers_df$Type)) <- levels(Aggregate_BothTrailers_df$Type)[2]

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggBoth_Affect_GT_rank <-lm(rank(GrossM1) ~ 
         + Type                      
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
            , data = Aggregate_BothTrailers_df)

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggBoth_Choice_GT_rank <- lm(rank(GrossM1) ~ 
         + Type
         + scale(W_score_scaled) 
         + Type:scale(W_score_scaled)  
            , data = Aggregate_BothTrailers_df)

# Create aggregate model for comedy neuro seq (log) controlling for number of theaters.
AggBoth_Seq_GT_rank <- lm(rank(GrossM1) ~ 
         + Type
         + scale(NAcc_seg1) 
         + scale(AIns_seg3)
         + scale(MPFC_seg5)
         + Type:scale(NAcc_seg1)
         + Type:scale(AIns_seg3)
         + Type:scale(MPFC_seg5)
            , data = Aggregate_BothTrailers_df)

# Create aggregate model for comedy neuro seq (log) and affect controlling for number of theaters.
AggBoth_SeqAffect_GT_rank <- lm(rank(GrossM1) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_seg1) 
         + scale(AIns_seg3)
         + scale(MPFC_seg5)
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_seg1)
         + Type:scale(AIns_seg3)
         + Type:scale(MPFC_seg5)
            , data = Aggregate_BothTrailers_df) 


AggBoth_ChoiceSeq_GT_rank <- lm(rank(GrossM1) ~ 
         + Type                        
         + scale(W_score_scaled) 
         + scale(NAcc_seg1) 
         + scale(AIns_seg3)
         + scale(MPFC_seg5)
         + Type:scale(W_score_scaled) 
         + Type:scale(NAcc_seg1)
         + Type:scale(AIns_seg3)
         + Type:scale(MPFC_seg5)
            , data = Aggregate_BothTrailers_df) 

AggBoth_Seq_list = list(
  "Affect GM1" = AggBoth_Affect_GT_rank, 
  "Choice GM1" = AggBoth_Choice_GT_rank,
  "Neuro Seq GM1" = AggBoth_Seq_GT_rank,
  "Affect Neuro Seq GM1" = AggBoth_SeqAffect_GT_rank,
  "Choice Neuro Seq GM1" = AggBoth_ChoiceSeq_GT_rank)

AggBoth_Seq_models <- modelsummary(AggBoth_Seq_list, stars=TRUE, 
                               statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #output="dataframe",
                               output="html",
                               gof_omit = "F|RMSE|Log") #%>% select(-part, -statistic)

print(contrasts(Aggregate_BothTrailers_df$Type))
AggBoth_Seq_models

```

```{r, echo=FALSE}
ggplot(Aggregate_BothTrailers_df, aes(x = (NAcc_seg1), y = rank(Gross_US_M1), color=Type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor() +
  geom_text(aes(label = Trailer), vjust = 2)
```


## AggBoth: Modal Peak (MP) Models.
```{r, echo=FALSE}

Aggregate_BothTrailers_df <- mutate(Aggregate_BothTrailers_df, Type = factor(Type, levels = c("horror", "comedy")))
contrasts(Aggregate_BothTrailers_df$Type) <- rbind(-1, 1)
colnames(contrasts(Aggregate_BothTrailers_df$Type)) <- levels(Aggregate_BothTrailers_df$Type)[2]

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggBoth_Affect_GT_rank <- lm(rank(GrossM1) ~ 
         + Type                      
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
            , data = Aggregate_BothTrailers_df)

# Create aggregate model for first month gross (log) controlling for number of theaters.
AggBoth_Choice_GT_rank <- lm(rank(GrossM1) ~ 
         + Type
         + scale(W_score_scaled) 
         + Type:scale(W_score_scaled)  
            , data = Aggregate_BothTrailers_df)

# Create aggregate model for comedy neuro seq (log) controlling for number of theaters.
AggBoth_MP_GT_rank <- lm(rank(GrossM1) ~ 
         + Type
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2) 
         + scale(MPFC_avg_peak_yes_pos2) 
         + Type:scale(NAcc_avg_peak_yes_pos2) 
         + Type:scale(AIns_avg_peak_yes_pos2)
         + Type:scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_BothTrailers_df )
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

# Create aggregate model for comedy neuro seq (log) and affect controlling for number of theaters.
AggBoth_MPAffect_GT_rank <- lm(rank(GrossM1) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2) 
         + scale(MPFC_avg_peak_yes_pos2) 
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_avg_peak_yes_pos2) 
         + Type:scale(AIns_avg_peak_yes_pos2)
         + Type:scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_BothTrailers_df)
          #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_ChoiceMPA_GT_rank <- lm(rank(GrossM1) ~ 
         + Type                        
         + scale(W_score_scaled) 
         + scale(NAcc_avg_peak_yes_pos2) 
         + scale(AIns_avg_peak_yes_pos2) 
         + scale(MPFC_avg_peak_yes_pos2) 
         + Type:scale(W_score_scaled) 
         + Type:scale(NAcc_avg_peak_yes_pos2) 
         + Type:scale(AIns_avg_peak_yes_pos2)
         + Type:scale(MPFC_avg_peak_yes_pos2)
            , data = Aggregate_BothTrailers_df) 
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_MP_list = list(
  "Affect GM1" = AggBoth_Affect_GT_rank, 
  "Choice GM1" = AggBoth_Choice_GT_rank,
  "Neuro MP GM1" = AggBoth_MP_GT_rank,
  "Affect Neuro MP GM1" = AggBoth_MPAffect_GT_rank,
  "Choice Neuro MP GM1" = AggBoth_ChoiceMPA_GT_rank)

AggBoth_MP_models <- modelsummary(AggBoth_MP_list, stars=TRUE, 
                               statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #output="dataframe",
                               output="html",
                               gof_omit = "F|RMSE|Log") #%>% select(-part, -statistic)

print(contrasts(Aggregate_BothTrailers_df$Type))
AggBoth_MP_models

```

```{r,  echo=FALSE}
ggplot(Aggregate_BothTrailers_df, aes(x = (NAcc_avg_peak_yes_pos2), y = rank(Gross_US_M1), color=Type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor() +
  geom_text(aes(label = Trailer), vjust = 2)
```






