---
title: "LMM_NF"
output: html_document
date: "2024-02-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
```


```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
```

Read dataset
```{r}
AllSubs_NeuralActivation <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_rm_outliers.csv')
```

# M1: Behavioral data 
```{r, echo = FALSE}
M1 <- lmer(scale(W_score_scaled) ~ Type +
           + scale(Pos_arousal_scaled) 
           + scale(Neg_arousal_scaled) 
           + Type:scale(Neg_arousal_scaled)  
           + Type:scale(Pos_arousal_scaled)  
           + (1|Participant) + (1|Trailer), 
           data = AllSubs_NeuralActivation%>% mutate(Type = factor(Type, levels = c("Horror", "Comedy")))
           )
summary(M1)
r.squaredGLMM(M1)
AIC(M1)
```

# M2: Neural data whole 
```{r, echo = FALSE}
M2 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_whole)
             + scale(AIns_whole) 
             + scale(MPFC_whole) 
             + Type:scale(NAcc_whole) 
             + Type:scale(AIns_whole) 
             + Type:scale(MPFC_whole) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M2)
r.squaredGLMM(M2)
AIC(M2)
```

# M3: Neural data whole + behavioral data
```{r, echo = FALSE}
M3 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_whole) 
             + scale(AIns_whole) 
             + scale(MPFC_whole)  
             + Type:scale(Pos_arousal_scaled)  
             + Type:scale(Neg_arousal_scaled)  
             + Type:scale(NAcc_whole)  
             + Type:scale(AIns_whole)  
             + Type:scale(MPFC_whole) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M3)
r.squaredGLMM(M3)
AIC(M3)
```

# M4: Neural data onset
```{r, echo = FALSE}
M4 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_onset) 
             + scale(AIns_onset) 
             + scale(MPFC_onset) + 
             + Type:scale(NAcc_onset)  
             + Type:scale(AIns_onset)  
             + Type:scale(MPFC_onset) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M4)
r.squaredGLMM(M4)
AIC(M4)
```

# M5: Neural data onset + behavioral data
```{r, echo = FALSE}
M5 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_onset)  
             + scale(AIns_onset)  
             + scale(MPFC_onset)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(Pos_arousal_scaled)  
             + Type:scale(NAcc_onset) 
             + Type:scale(AIns_onset)  
             + Type:scale(MPFC_onset) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M5)
r.squaredGLMM(M5)
AIC(M5)
```

# M6: Neural data offset
```{r, echo = FALSE}
M6 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_offset) 
             + scale(AIns_offset) 
             + scale(MPFC_offset)  
             + Type:scale(NAcc_offset) 
             + Type:scale(AIns_offset)  
             + Type:scale(MPFC_offset) 
             + (1|Participant) + (1|Trailer) 
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M6)
r.squaredGLMM(M6)
AIC(M6)
```

# M7: Neural data offset + behavioral data
```{r, echo = FALSE}
M7 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_offset) 
             + scale(AIns_offset) 
             + scale(MPFC_offset)  
             + Type:scale(Pos_arousal_scaled)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(NAcc_offset) 
             + Type:scale(AIns_offset)  
             + Type:scale(MPFC_offset) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M7)
r.squaredGLMM(M7)
AIC(M7)
```

# M7: Neural data middle
```{r, echo = FALSE}
# seven is repeated
M7 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_middle) 
             + scale(AIns_middle) 
             + scale(MPFC_middle)  
             + Type:scale(NAcc_middle)  
             + Type:scale(AIns_middle)  
             + Type:scale(MPFC_middle)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M7)
r.squaredGLMM(M7)
AIC(M7)
```

# M8: Neural data middle + behavioral data
```{r, echo = FALSE}
M8 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_middle) 
             + scale(AIns_middle) 
             + scale(MPFC_middle)  
             + Type:scale(Neg_arousal_scaled)  
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(NAcc_middle)  
             + Type:scale(AIns_middle)  
             + Type:scale(MPFC_middle)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M8)
r.squaredGLMM(M8)
AIC(M8)
```

# M9: Neural ISC data 
```{r, echo = FALSE}
M9 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_ISC) 
             + scale(AIns_ISC) 
             + scale(MPFC_ISC) 
             + Type:scale(NAcc_ISC)  
             + Type:scale(AIns_ISC) 
             + Type:scale(MPFC_ISC) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M9)
r.squaredGLMM(M9)
AIC(M9)
```

# M10: Neural ISC data + behavioral data
```{r, echo = FALSE}
M10 <- lmer(scale(W_score_scaled) ~ Type  
             + scale(Pos_arousal_scaled)  
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_ISC) 
             + scale(AIns_ISC)  
             + scale(MPFC_ISC)  
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(NAcc_ISC)  
             + Type:scale(AIns_ISC)  
             + Type:scale(MPFC_ISC)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M10)
r.squaredGLMM(M10)
AIC(M10)
```

# Sequence Test
# NAcc onset and AIns offset.
# M11: Neural seq data 
```{r, echo = FALSE}
M11 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_onset) 
             + scale(AIns_offset) 
              
             + Type:scale(NAcc_onset)  
             + Type:scale(AIns_offset) 
         
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M11)
r.squaredGLMM(M11)
```

# M12: Neural seq data + behavioral data
```{r, echo = FALSE}
M12 <- lmer(scale(W_score_scaled) ~ Type  
             + scale(Pos_arousal_scaled)  
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_middle) 
             + scale(AIns_offset)  
             + scale(MPFC_offset)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(NAcc_middle)  
             + Type:scale(AIns_offset)  
             + Type:scale(MPFC_offset)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M12)
r.squaredGLMM(M10)
```
