---
title: "LMM_NF"
output: html_document
date: "2024-02-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
```


```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
```

# Read dataset
```{r}
AllSubs_NeuralActivation <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC.csv')

AllSubs_NeuralActivation_Horror <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC_Horror.csv')

AllSubs_NeuralActivation_Comedy <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC_Comedy.csv')

```

# Create data frames for each model.
```{r}

All_W <- AllSubs_NeuralActivation$W_score_scaled
Comedy_W <- AllSubs_NeuralActivation_Comedy$W_score_scaled
Horror_W <- AllSubs_NeuralActivation_Horror$W_score_scaled

All_PA <- AllSubs_NeuralActivation$Pos_arousal_scaled
Comedy_PA <- AllSubs_NeuralActivation_Comedy$Pos_arousal_scaled
Horror_PA <- AllSubs_NeuralActivation_Horror$Pos_arousal_scaled

All_NA <- AllSubs_NeuralActivation$Neg_arousal_scaled
Comedy_NA <- AllSubs_NeuralActivation_Comedy$Neg_arousal_scaled
Horror_NA <- AllSubs_NeuralActivation_Horror$Neg_arousal_scaled

M1_df <- data.frame(All_W, All_PA, All_NA) 
M1_C_df <- data.frame(Comedy_W, Comedy_PA, Comedy_NA) 
M1_H_df <- data.frame(Horror_W, Horror_PA, Horror_NA) 

```

```{r}
# Define whole variables. 
All_NAcc_whole <- AllSubs_NeuralActivation$NAcc_whole
All_AIns_whole <- AllSubs_NeuralActivation$AIns_whole
All_MPFC_whole <- AllSubs_NeuralActivation$MPFC_whole

Comedy_NAcc_whole <- AllSubs_NeuralActivation_Comedy$NAcc_whole
Comedy_AIns_whole <- AllSubs_NeuralActivation_Comedy$AIns_whole
Comedy_MPFC_whole <- AllSubs_NeuralActivation_Comedy$MPFC_whole

Horror_NAcc_whole <- AllSubs_NeuralActivation_Horror$NAcc_whole
Horror_AIns_whole <- AllSubs_NeuralActivation_Horror$AIns_whole
Horror_MPFC_whole <- AllSubs_NeuralActivation_Horror$MPFC_whole

# Define models. 

M3_df <- data.frame(All_W, All_PA, All_NA, All_NAcc_whole, All_AIns_whole, All_MPFC_whole) 
M3_C_df <- data.frame(Comedy_W, Comedy_PA, Comedy_NA, Comedy_NAcc_whole,
                      Comedy_AIns_whole, Comedy_MPFC_whole) 
M3_H_df <- data.frame(Horror_W, Horror_PA, Horror_NA, Horror_NAcc_whole,
                      Horror_AIns_whole, Horror_MPFC_whole) 
```

```{r}
# Define onset variables. 
All_NAcc_onset <- AllSubs_NeuralActivation$NAcc_onset
All_AIns_onset <- AllSubs_NeuralActivation$AIns_onset
All_MPFC_onset <- AllSubs_NeuralActivation$MPFC_onset

Comedy_NAcc_onset <- AllSubs_NeuralActivation_Comedy$NAcc_onset
Comedy_AIns_onset <- AllSubs_NeuralActivation_Comedy$AIns_onset
Comedy_MPFC_onset <- AllSubs_NeuralActivation_Comedy$MPFC_onset

Horror_NAcc_onset <- AllSubs_NeuralActivation_Horror$NAcc_onset
Horror_AIns_onset <- AllSubs_NeuralActivation_Horror$AIns_onset
Horror_MPFC_onset <- AllSubs_NeuralActivation_Horror$MPFC_onset

# Define models. 
M5_df <- data.frame(All_W, All_PA, All_NA, All_NAcc_onset, All_AIns_onset, All_MPFC_onset) 
M5_C_df <- data.frame(Comedy_W, Comedy_PA, Comedy_NA, Comedy_NAcc_onset,
                      Comedy_AIns_onset, Comedy_MPFC_onset) 
M5_H_df <- data.frame(Horror_W, Horror_PA, Horror_NA, Horror_NAcc_onset,
                      Horror_AIns_onset, Horror_MPFC_onset) 
```

```{r}
# Define offset variables. 
All_NAcc_offset <- AllSubs_NeuralActivation$NAcc_offset
All_AIns_offset <- AllSubs_NeuralActivation$AIns_offset
All_MPFC_offset <- AllSubs_NeuralActivation$MPFC_offset

Comedy_NAcc_offset <- AllSubs_NeuralActivation_Comedy$NAcc_offset
Comedy_AIns_offset <- AllSubs_NeuralActivation_Comedy$AIns_offset
Comedy_MPFC_offset <- AllSubs_NeuralActivation_Comedy$MPFC_offset

Horror_NAcc_offset <- AllSubs_NeuralActivation_Horror$NAcc_offset
Horror_AIns_offset <- AllSubs_NeuralActivation_Horror$AIns_offset
Horror_MPFC_offset <- AllSubs_NeuralActivation_Horror$MPFC_offset

# Define models. 
M7_df <- data.frame(All_W, All_PA, All_NA, All_NAcc_offset, All_AIns_offset, All_MPFC_offset) 
M7_C_df <- data.frame(Comedy_W, Comedy_PA, Comedy_NA, Comedy_NAcc_offset,
                      Comedy_AIns_offset, Comedy_MPFC_offset) 
M7_H_df <- data.frame(Horror_W, Horror_PA, Horror_NA, Horror_NAcc_offset,
                      Horror_AIns_offset, Horror_MPFC_offset) 
```


```{r}
# Define middle variables. 
All_NAcc_middle <- AllSubs_NeuralActivation$NAcc_middle
All_AIns_middle <- AllSubs_NeuralActivation$AIns_middle
All_MPFC_middle <- AllSubs_NeuralActivation$MPFC_middle

Comedy_NAcc_middle <- AllSubs_NeuralActivation_Comedy$NAcc_middle
Comedy_AIns_middle <- AllSubs_NeuralActivation_Comedy$AIns_middle
Comedy_MPFC_middle <- AllSubs_NeuralActivation_Comedy$MPFC_middle

Horror_NAcc_middle <- AllSubs_NeuralActivation_Horror$NAcc_middle
Horror_AIns_middle <- AllSubs_NeuralActivation_Horror$AIns_middle
Horror_MPFC_middle <- AllSubs_NeuralActivation_Horror$MPFC_middle

# Define models. 
M9_df <- data.frame(All_W, All_PA, All_NA, All_NAcc_middle, All_AIns_middle, All_MPFC_middle) 
M9_C_df <- data.frame(Comedy_W, Comedy_PA, Comedy_NA, Comedy_NAcc_middle,
                      Comedy_AIns_middle, Comedy_MPFC_middle) 
M9_H_df <- data.frame(Horror_W, Horror_PA, Horror_NA, Horror_NAcc_middle,
                      Horror_AIns_middle, Horror_MPFC_middle) 
```

```{r}
# Define ISC variables. 
All_NAcc_ISC <- AllSubs_NeuralActivation$NAcc_ISC
All_AIns_ISC <- AllSubs_NeuralActivation$AIns_ISC
All_MPFC_ISC <- AllSubs_NeuralActivation$MPFC_ISC

Comedy_NAcc_ISC <- AllSubs_NeuralActivation_Comedy$NAcc_ISC
Comedy_AIns_ISC <- AllSubs_NeuralActivation_Comedy$AIns_ISC
Comedy_MPFC_ISC <- AllSubs_NeuralActivation_Comedy$MPFC_ISC

Horror_NAcc_ISC <- AllSubs_NeuralActivation_Horror$NAcc_ISC
Horror_AIns_ISC <- AllSubs_NeuralActivation_Horror$AIns_ISC
Horror_MPFC_ISC <- AllSubs_NeuralActivation_Horror$MPFC_ISC

# Define models. 
M11_df <- data.frame(All_W, All_PA, All_NA, All_NAcc_ISC, All_AIns_ISC, All_MPFC_ISC) 
M11_C_df <- data.frame(Comedy_W, Comedy_PA, Comedy_NA, Comedy_NAcc_ISC, Comedy_AIns_ISC, Comedy_MPFC_ISC) 
M11_H_df <- data.frame(Horror_W, Horror_PA, Horror_NA, Horror_NAcc_ISC, Horror_AIns_ISC, Horror_MPFC_ISC) 
```

# Plotting stuff. 
```{r}

ggplot(AllSubs_NeuralActivation, aes(x=NAcc_ISC, y = (W_score_scaled), fill=Type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor()

```


# M1: Behavioral data 
```{r, echo = FALSE}
M1 <- lmer(scale(W_score_scaled) ~ Type +
           + scale(Pos_arousal_scaled) 
           + scale(Neg_arousal_scaled) 
           + Type:scale(Neg_arousal_scaled)  
           + Type:scale(Pos_arousal_scaled)  
           + (1|Participant) + (1|Trailer), 
           data = AllSubs_NeuralActivation%>% mutate(Type = factor(Type, levels = c("Horror", "Comedy")))
           )
summary(M1)
r.squaredGLMM(M1)
AIC(M1)

# Create pairs plot. 
ggpairs(M1_df)
ggpairs(M1_C_df)
ggpairs(M1_H_df)
```

# M2: Neural data whole 
```{r, echo = FALSE}
M2 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_whole)
             + scale(AIns_whole) 
             + scale(MPFC_whole) 
             + Type:scale(NAcc_whole) 
             + Type:scale(AIns_whole) 
             + Type:scale(MPFC_whole) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M2)
r.squaredGLMM(M2)
AIC(M2)
```

# M3: Neural data whole + behavioral data
```{r, echo = FALSE}
M3 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_whole) 
             + scale(AIns_whole) 
             + scale(MPFC_whole)  
             + Type:scale(Pos_arousal_scaled)  
             + Type:scale(Neg_arousal_scaled)  
             + Type:scale(NAcc_whole)  
             + Type:scale(AIns_whole)  
             + Type:scale(MPFC_whole) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M3)
r.squaredGLMM(M3)
AIC(M3)

# Create pairs plot. 
#ggpairs(M3_df)
#ggpairs(M3_C_df)
#ggpairs(M3_H_df)
```

# M4: Neural data onset
```{r, echo = FALSE}
M4 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_onset) 
             + scale(AIns_onset) 
             + scale(MPFC_onset) + 
             + Type:scale(NAcc_onset)  
             + Type:scale(AIns_onset)  
             + Type:scale(MPFC_onset) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M4)
r.squaredGLMM(M4)
AIC(M4)
```

# M5: Neural data onset + behavioral data
```{r, echo = FALSE}
M5 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_onset)  
             + scale(AIns_middle)  
             + scale(MPFC_offset)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(Pos_arousal_scaled)  
             + Type:scale(NAcc_onset) 
             + Type:scale(AIns_middle)  
             + Type:scale(MPFC_offset) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M5)
r.squaredGLMM(M5)
AIC(M5)

# Create pairs plot. 
#ggpairs(M5_df)
#ggpairs(M5_C_df)
#ggpairs(M5_H_df)
```

# M6: Neural data offset
```{r, echo = FALSE}
M6 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_offset) 
             + scale(AIns_offset) 
             + scale(MPFC_offset)  
             + Type:scale(NAcc_offset) 
             + Type:scale(AIns_offset)  
             + Type:scale(MPFC_offset) 
             + (1|Participant) + (1|Trailer) 
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M6)
r.squaredGLMM(M6)
AIC(M6)
```

# M7: Neural data offset + behavioral data
```{r, echo = FALSE}
M7 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_offset) 
             + scale(AIns_offset) 
             + scale(MPFC_offset)  
             + Type:scale(Pos_arousal_scaled)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(NAcc_offset) 
             + Type:scale(AIns_offset)  
             + Type:scale(MPFC_offset) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M7)
r.squaredGLMM(M7)
AIC(M7)

# Create pairs plot. 
#ggpairs(M7_df)
#ggpairs(M7_C_df)
#ggpairs(M7_H_df)
```

# M8: Neural data middle
```{r, echo = FALSE}
# seven is repeated
M8 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_middle) 
             + scale(AIns_middle) 
             + scale(MPFC_middle)  
             + Type:scale(NAcc_middle)  
             + Type:scale(AIns_middle)  
             + Type:scale(MPFC_middle)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M8)
r.squaredGLMM(M8)
AIC(M8)
```

# M9: Neural data middle + behavioral data
```{r, echo = FALSE}
M9 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_middle) 
             + scale(AIns_middle) 
             + scale(MPFC_middle)  
             + Type:scale(Neg_arousal_scaled)  
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(NAcc_middle)  
             + Type:scale(AIns_middle)  
             + Type:scale(MPFC_middle)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M9)
r.squaredGLMM(M9)
AIC(M9)

# Create pairs plot. 
#ggpairs(M9_df)
#ggpairs(M9_C_df)
#ggpairs(M9_H_df)
```

# M10: Neural ISC data 
```{r, echo = FALSE}
M10 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_ISC) 
             + scale(AIns_ISC) 
             + scale(MPFC_ISC) 
             + Type:scale(NAcc_ISC)  
             + Type:scale(AIns_ISC) 
             + Type:scale(MPFC_ISC) 
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M10)
r.squaredGLMM(M10)
AIC(M10)
```

# M11: Neural ISC data + behavioral data
```{r, echo = FALSE}
M11 <- lmer(scale(W_score_scaled) ~ Type  
             + scale(Pos_arousal_scaled)  
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_ISC) 
             + scale(AIns_ISC)  
             + scale(MPFC_ISC)  
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(NAcc_ISC)  
             + Type:scale(AIns_ISC)  
             + Type:scale(MPFC_ISC)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M11)
r.squaredGLMM(M11)
AIC(M11)

# Create pairs plot. 
#ggpairs(M11_df)
#ggpairs(M11_C_df)
#ggpairs(M11_H_df)
```

# Sequence Test
# NAcc onset and AIns offset.
# M11: Neural seq data 
```{r, echo = FALSE}
M12 <- lmer(scale(W_score_scaled) ~ Type 
             + scale(NAcc_onset) 
             + scale(AIns_offset) 
              
             + Type:scale(NAcc_onset)  
             + Type:scale(AIns_offset) 
         
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M12)
r.squaredGLMM(M12)
```

# M12: Neural seq data + behavioral data
```{r, echo = FALSE}
M12 <- lmer(scale(W_score_scaled) ~ Type  
             + scale(Pos_arousal_scaled)  
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_middle) 
             + scale(AIns_offset)  
             + scale(MPFC_middle)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(NAcc_middle)  
             + Type:scale(AIns_offset)  
             + Type:scale(MPFC_middle)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M12)
r.squaredGLMM(M12)
```
```{r, echo = FALSE}
M12 <- lmer(scale(W_score_scaled) ~ Type  
             + scale(Pos_arousal_scaled)  
             + scale(Neg_arousal_scaled) 
             + scale(NAcc_ind_peaks_pos) 
             + scale(AIns_ind_peaks_pos)  
             + scale(MPFC_ind_peaks_pos)  
             + Type:scale(Neg_arousal_scaled) 
             + Type:scale(Pos_arousal_scaled) 
             + Type:scale(NAcc_ind_peaks_pos)  
             + Type:scale(AIns_ind_peaks_pos)  
             + Type:scale(MPFC_ind_peaks_pos)  
             + (1|Participant) + (1|Trailer)
             , data = AllSubs_NeuralActivation %>% mutate(Type = factor(Type, levels = c("Horror", "Comedy"))))
summary(M12)
r.squaredGLMM(M12)
```