---
title: "R Notebook"
output: html_notebook
---

# Load libraries
```{r, warning = FALSE, message = FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
library(car)
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
library(modelsummary)
library(pandoc)
library(tinytable)
```

# Read dataset
```{r}
AllSubs_IndividualChoice_C <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_ISC_Comedy.csv')
```

# M1_C: Behavioral data
```{r, echo = FALSE}
M1_C <- lmer(scale(W_score_scaled) ~ scale(Pos_arousal_scaled) + scale(Neg_arousal_scaled) + 
             (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
#summary(M1_C)
#r.squaredGLMM(M1_C)
#confint(M1_C)
#AIC(M1_C)
```

# Neural ISC 
```{r, echo = FALSE}
M2_C <- lmer(scale(W_score_scaled) ~ 
               #scale(NAcc_ISC) + 
               scale(AIns_ISC) + 
               scale(MPFC_ISC) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)

M3_C <- lmer(scale(W_score_scaled) ~ 
               scale(Pos_arousal_scaled) + 
               scale(Neg_arousal_scaled) + 
               #scale(NAcc_ISC) + 
               scale(AIns_ISC) + 
               scale(MPFC_ISC) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)

ISC_list <- list(
  "Affect" = M1_C, 
  "Neuro ISC" = M2_C, 
  "Affect & Neuro ISC" = M3_C)

ISC_models <- modelsummary(ISC_list, stars=TRUE, statistic=NULL, output = "dataframe", gof_omit = "F|RMSE|Log") %>% select(-part, -statistic)
ISC_models

```
Are NAcc_ISC and MPFC co-linear? 
```{r}
ggplot(AllSubs_IndividualChoice_C, aes(x = NAcc_ISC, y = (MPFC_ISC))) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor() 
  #geom_text(aes(label = Trailer), vjust = 2)
```


# Neural sequence models
```{r, echo = FALSE}
M4_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_onset) + 
               scale(AIns_middle) + 
               scale(MPFC_offset) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)

M5_C <- lmer(scale(W_score_scaled) ~ 
               scale(Pos_arousal_scaled) + 
               scale(Neg_arousal_scaled) + 
               scale(NAcc_onset) + 
               scale(AIns_middle) + 
               scale(MPFC_offset) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)

Seq_list <- list(
  "Affect" = M1_C, 
  "Neuro seq" = M4_C, 
  "Affect & Neuro seq" = M5_C)

Seq_models <- modelsummary(Seq_list, stars=TRUE, statistic=NULL, output = "dataframe", gof_omit = "F|RMSE|Log") %>% select(-part, -statistic)
Seq_models
```

# Neural dem peaks
```{r, echo = FALSE}
M6_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_dem_peak_pos_yes) + 
               #scale(AIns_dem_peak_pos_yes) + 
               #scale(MPFC_dem_peak_pos_yes) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)

M7_C <- lmer(scale(W_score_scaled) ~ 
               scale(Pos_arousal_scaled) + 
               scale(Neg_arousal_scaled) + 
               scale(NAcc_dem_peak_pos_yes) + 
               #scale(AIns_dem_peak_pos_yes) + 
               #scale(MPFC_dem_peak_pos_yes) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)

Dem_peaks_list <- list(
  "Affect" = M1_C, 
  "Neuro dem peaks" = M6_C, 
  "Affect & Neuro dem peaks" = M7_C)

Dem_peaks_list <- modelsummary(Dem_peaks_list, stars=TRUE, statistic=NULL, output = "dataframe", gof_omit = "F|RMSE|Log") %>% select(-part, -statistic)
Dem_peaks_list
```


# M5_C: Neural activation (onset) + Behavioral data
```{r, echo = FALSE}
M5_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_onset) 
              + scale(AIns_onset) 
              + scale(MPFC_onset) 
              + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M5_C)
r.squaredGLMM(M5_C)
confint(M5_C)
AIC(M5_C)
```

# M6_C: Neural activation (middle)
```{r, echo = FALSE}
M6_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_middle) + 
               scale(AIns_middle) + 
               scale(MPFC_middle) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M6_C)
r.squaredGLMM(M6_C)
confint(M6_C)
AIC(M6_C)
```

# M7_C: Neural activation (middle) + Behavioral data
```{r, echo = FALSE}
M7_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_middle) 
              + scale(AIns_middle) 
              + scale(MPFC_middle) 
              + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M7_C)
r.squaredGLMM(M7_C)
confint(M7_C)
AIC(M7_C)
```

# M8_C: Neural activation (offset)
```{r, echo = FALSE}
M8_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_offset) + 
               scale(AIns_offset) + 
               scale(MPFC_offset) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M8_C)
r.squaredGLMM(M8_C)
confint(M8_C)
AIC(M8_C)
```

# M9_C: Neural activation (offset) + Behavioral data
```{r, echo = FALSE}

optimal_NAcc_df <- mutate(AllSubs_IndividualChoice_C, 
                          NAcc_opt = rowMeans(select(AllSubs_IndividualChoice_C, 
                          c("NAcc_TR5", "NAcc_TR6", "NAcc_TR7", "NAcc_TR8"))))


M9_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_onset) 
              #+ scale(AIns_middle) 
              + scale(MPFC_middle) 
              + (1|Participant) + (1|Trailer), data = optimal_NAcc_df)
summary(M9_C)
r.squaredGLMM(M9_C)
AIC(M9_C)
#optimal_NAcc_df
```

# M10_C: Neural ISC 
```{r, echo = FALSE}
M10_C <- lmer(scale(W_score_scaled) ~ 
               + scale(NAcc_ISC) 
               + scale(AIns_ISC) 
               + scale(MPFC_ISC) 
               + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M10_C)
r.squaredGLMM(M10_C)
AIC(M10_C)
vif(M10_C)
```

# M11_C: Neural ISC + Behavioral data
```{r, echo = FALSE}
M11_C <- lmer(scale(W_score_scaled)~ 
               + scale(Pos_arousal_scaled) 
               + scale(Neg_arousal_scaled)
               + scale(NAcc_ISC) 
               + scale(AIns_ISC) 
               + scale(MPFC_ISC) 
               + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M11_C)
r.squaredGLMM(M11_C)
AIC(M11_C)
vif(M11_C)
```



# M8_C: Neural activation (offset)
```{r, echo = FALSE}
M8_C <- lmer(scale(W_score_scaled) ~ 
               scale(Pos_arousal_scaled) +
               scale(Neg_arousal_scaled) +
               scale(NAcc_ind_peaks_pos) +
               scale(AIns_ind_peaks_pos) + # 5
               scale(MPFC_ind_peaks_pos) + # 7
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M8_C)
r.squaredGLMM(M8_C)
#confint(M8_C)
AIC(M8_C)
```

```{r}
optimal_NAcc_df <- mutate(AllSubs_IndividualChoice_C, 
                          NAcc_opt = rowMeans(select(AllSubs_IndividualChoice_C, 
                          c("NAcc_TR5", "NAcc_TR6", "NAcc_TR7", "NAcc_TR8"))))

# na.rm = TRUE
ggplot(optimal_NAcc_df, aes(x=NAcc_dem_peak_pos_yes, y = (W_score_scaled))) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor()
```

