---
title: "R Notebook"
output: html_notebook
---

# Load libraries
```{r, warning = FALSE, message = FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
```

# Read dataset
```{r}
AllSubs_IndividualChoice_C <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Comedy.csv')
```

# M1_C: Behavioral data
```{r, echo = FALSE}
M1_C <- lmer(scale(W_score_scaled) ~ scale(Pos_arousal_scaled) + scale(Neg_arousal_scaled) + 
             (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M1_C)
r.squaredGLMM(M1_C)
confint(M1_C)
AIC(M1_C)
```

# M2_C: Neural activation (whole)
```{r, echo = FALSE}
M2_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_whole) + 
               scale(AIns_whole) + 
               scale(MPFC_whole) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M2_C)
r.squaredGLMM(M2_C)
confint(M2_C)
AIC(M2_C)
```

# M3_C: Neural activation (whole) + Behavioral data
```{r, echo = FALSE}
M3_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_whole) 
              + scale(AIns_whole) 
              + scale(MPFC_whole) 
              + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M3_C)
r.squaredGLMM(M3_C)
confint(M3_C)
AIC(M3_C)
```

# M4_C: Neural activation (onset)
```{r, echo = FALSE}
M4_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_onset) + 
               scale(AIns_onset) + 
               scale(MPFC_onset) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M4_C)
r.squaredGLMM(M4_C)
confint(M4_C)
AIC(M4_C)
```

# M5_C: Neural activation (onset) + Behavioral data
```{r, echo = FALSE}
M5_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_onset) 
              + scale(AIns_onset) 
              + scale(MPFC_onset) 
              + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M5_C)
r.squaredGLMM(M5_C)
confint(M5_C)
AIC(M5_C)
```

# M6_C: Neural activation (middle)
```{r, echo = FALSE}
M6_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_middle) + 
               scale(AIns_middle) + 
               scale(MPFC_middle) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M6_C)
r.squaredGLMM(M6_C)
confint(M6_C)
AIC(M6_C)
```

# M7_C: Neural activation (middle) + Behavioral data
```{r, echo = FALSE}
M7_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_middle) 
              + scale(AIns_middle) 
              + scale(MPFC_middle) 
              + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M7_C)
r.squaredGLMM(M7_C)
confint(M7_C)
AIC(M7_C)
```

# M8_C: Neural activation (offset)
```{r, echo = FALSE}
M8_C <- lmer(scale(W_score_scaled) ~ 
               scale(NAcc_offset) + 
               scale(AIns_offset) + 
               scale(MPFC_offset) +
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M8_C)
r.squaredGLMM(M8_C)
confint(M8_C)
AIC(M8_C)
```

# M9_C: Neural activation (offset) + Behavioral data
```{r, echo = FALSE}
M9_C <- lmer(scale(W_score_scaled) ~ 
              + scale(Pos_arousal_scaled) 
              + scale(Neg_arousal_scaled) 
              + scale(NAcc_offset) 
              + scale(AIns_offset) 
              + scale(MPFC_offset) 
              + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M9_C)
r.squaredGLMM(M9_C)
confint(M9_C)
AIC(M9_C)
```

# M10_C: Neural ISC 
```{r, echo = FALSE}
M10_C <- lmer(scale(W_score_scaled) ~ 
               + scale(NAcc_ISC) 
               + scale(AIns_ISC) 
               + scale(MPFC_ISC) 
               + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M10_C)
r.squaredGLMM(M10_C)
AIC(M10_C)
```

# M11_C: Neural ISC + Behavioral data
```{r, echo = FALSE}
M11_C <- lmer(scale(W_score_scaled)~ 
               + scale(Pos_arousal_scaled) 
               + scale(Neg_arousal_scaled)
               + scale(NAcc_ISC) 
               + scale(AIns_ISC) 
               + scale(MPFC_ISC) 
               # + scale(Pos_arousal):scale(NAcc_ISC) + 
               #scale(Pos_arousal):scale(AIns_ISC) +
               #scale(Pos_arousal):scale(MPFC_ISC) + 
               #scale(Neg_arousal):scale(NAcc_ISC) +
               #scale(Neg_arousal):scale(AIns_ISC) + 
               #scale(Neg_arousal):scale(MPFC_ISC) +
               + (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M11_C)
r.squaredGLMM(M11_C)
AIC(M11_C)
```



# M8_C: Neural activation (offset)
```{r, echo = FALSE}
M8_C <- lmer(scale(W_score_scaled) ~ 
               #scale(Pos_arousal_scaled) +
               #scale(Neg_arousal_scaled) +
               #scale(NAcc_TR4) + # 4
               #scale(AIns_TR5) + # 5
               #scale(MPFC_TR7) + # 7
            (1|Participant) + (1|Trailer), data = AllSubs_IndividualChoice_C)
summary(M8_C)
r.squaredGLMM(M8_C)
confint(M8_C)
AIC(M8_C)
```
