---
title: "R Notebook"
output: html_notebook
---
# Load libraries
```{r}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
```


```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
```
Read dataset
```{r}
AllSubs_NeuralActivation_H <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Horror.csv')
AllSubs_NeuralActivation_C <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Comedy.csv')
```
# M1_H: Behavioral data
```{r, echo = FALSE}
M1_H <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) + 
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M1_H)
r.squaredGLMM(M1_H)
```
# M1_C: Behavioral data
```{r, echo = FALSE}
M1_C <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) + 
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M1_C)
r.squaredGLMM(M1_C)
```
# M2_H: Neural activation (whole)
```{r, echo = FALSE}
M2_H <- lmer(W_score~ scale(NAcc_whole) + scale(AIns_whole) + scale(MPFC_whole) +
            (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M2_H)
r.squaredGLMM(M2_H)
```
# M2_C: Neural activation (whole)
```{r, echo = FALSE}
M2_C <- lmer(W_score~ scale(NAcc_whole) + scale(AIns_whole) + scale(MPFC_whole) +
            (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M2_C)
r.squaredGLMM(M2_C)
```
# M3_H: Neural activation (whole) + Behavioral data
```{r, echo = FALSE}
M3_H <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) +  
             scale(NAcc_whole) + scale(AIns_whole) + scale(MPFC_whole) + 
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M3_H)
r.squaredGLMM(M3_H)
```
# M3_C: Neural activation (whole) + Behavioral data
```{r, echo = FALSE}
M3_C <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) +  
             scale(NAcc_whole) + scale(AIns_whole) + scale(MPFC_whole) + 
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M3_C)
r.squaredGLMM(M3_C)
```
# M4_H: Neural ISC 
```{r, echo = FALSE}
M4_H <- lmer(W_score~ scale(NAcc_ISC) + scale(AIns_ISC) + scale(MPFC_ISC) +
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M4_H)
r.squaredGLMM(M4_H)
```
# M4_C: Neural ISC 
```{r, echo = FALSE}
M4_C <- lmer(W_score~ scale(NAcc_ISC) + scale(AIns_ISC) + scale(MPFC_ISC) +
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M4_C)
r.squaredGLMM(M4_C)
```
# M5_H: Neural ISC + Behavioral data
```{r, echo = FALSE}
M5_H <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) + 
             scale(NAcc_ISC) + scale(AIns_ISC) + scale(MPFC_ISC) +
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M5_H)
r.squaredGLMM(M5_H)
```
# M5_C: Neural ISC + Behavioral data
```{r, echo = FALSE}
M5_C <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) + 
             scale(NAcc_ISC) + scale(AIns_ISC) + scale(MPFC_ISC) +
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M5_C)
r.squaredGLMM(M5_C)
```
# M6_H: Neural activation (middle)
```{r, echo = FALSE}
M6_H <- lmer(W_score~ scale(NAcc_middle) + scale(AIns_middle) + scale(MPFC_middle) +
            (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M6_H)
r.squaredGLMM(M6_H)
```
# M6_C: Neural activation (middle)
```{r, echo = FALSE}
M6_C <- lmer(W_score~ scale(NAcc_middle) + scale(AIns_middle) + scale(MPFC_middle) +
            (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M6_C)
r.squaredGLMM(M6_C)
```
# M7_H: Neural activation (middle) + behavioral data
```{r, echo = FALSE}
M7_H <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) +  
             scale(NAcc_middle) + scale(AIns_middle) + scale(MPFC_middle) +
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_H)
summary(M7_H)
r.squaredGLMM(M7_H)
```
# M7_C: Neural activation (middle) + behavioral data
```{r, echo = FALSE}
M7_C <- lmer(W_score~ scale(Pos_arousal) + scale(Neg_arousal) +  
             scale(NAcc_middle) + scale(AIns_middle) + scale(MPFC_middle) +
             (1|Participant) + (1|Trailer), data = AllSubs_NeuralActivation_C)
summary(M7_C)
r.squaredGLMM(M7_C)
```


# Compare brhavioral and neural models
```{r}
#AIC(M1_H, M2_H, M3_H)
#```
# M3 Pairs plot 

#W_score <- AllSubs_NeuralActivation_H %>% pull(W_score)
#A_score <- AllSubs_NeuralActivation_H %>% pull(A_score)
#F_score <- AllSubs_NeuralActivation_H %>% pull(F_score)

#NAcc_whole <- AllSubs_NeuralActivation_H %>% pull(NAcc_whole)
#AIns_whole <- AllSubs_NeuralActivation_H %>% pull(AIns_whole)
#MPFC_whole <- AllSubs_NeuralActivation_H %>% pull(MPFC_whole)

#M3_data <- data.frame(W_score, A_score, F_score, NAcc_whole, AIns_whole, MPFC_whole) 

#ggpairs(M3_data)
```
