---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
library(car)
```


```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
```

# Read dataset
```{r}
AllSubs_NeuralActivation <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Aggregate_Combined_Horror_clean.csv')
```
# Create data frames for each model.
```{r}
# Define aggregate variables. 
GoT_W1 <- (log(AllSubs_NeuralActivation$Gross_US_W1_num) / AllSubs_NeuralActivation$Theaters_US_W1_num)
GoT_M1 <- rank(log(AllSubs_NeuralActivation$Gross_US_M1) / AllSubs_NeuralActivation$Theaters_US_M1)
GoT_total <- (log(AllSubs_NeuralActivation$Gross_Total_US) / AllSubs_NeuralActivation$Total_Theaters_US)

All_Gross_W1_log <- log(AllSubs_NeuralActivation$Gross_US_W1_num)
All_Theaters_W1 <- AllSubs_NeuralActivation$Theaters_US_W1_num

All_Gross_M1_log <- rank(log(AllSubs_NeuralActivation$Gross_US_M1))
All_Theaters_M1 <- AllSubs_NeuralActivation$Theaters_US_M1

# Define affect variables.
All_PA <- AllSubs_NeuralActivation$Pos_arousal_scaled
All_NA <- AllSubs_NeuralActivation$Neg_arousal_scaled

FW_US_M1_df <- data.frame(All_Gross_W1_log, All_Theaters_W1) 
FM_US_M14_df <- data.frame(All_Gross_M1_log, All_Theaters_M1) 
```
# Neural signals.  
```{r}
# Define ISC variables. 
All_NAcc_ISC <- AllSubs_NeuralActivation$NAcc_ISC
All_AIns_ISC <- AllSubs_NeuralActivation$AIns_ISC
All_MPFC_ISC <- AllSubs_NeuralActivation$MPFC_ISC

All_NAcc_whole <- AllSubs_NeuralActivation$NAcc_whole
All_AIns_whole <- AllSubs_NeuralActivation$AIns_whole
All_MPFC_whole <- AllSubs_NeuralActivation$MPFC_whole

All_NAcc_onset <- AllSubs_NeuralActivation$NAcc_onset
All_AIns_onset <- AllSubs_NeuralActivation$AIns_onset
All_MPFC_onset <- AllSubs_NeuralActivation$MPFC_onset

All_NAcc_middle <- AllSubs_NeuralActivation$NAcc_middle
All_AIns_middle <- AllSubs_NeuralActivation$AIns_middle
All_MPFC_middle <- AllSubs_NeuralActivation$MPFC_middle

All_NAcc_offset <- AllSubs_NeuralActivation$NAcc_offset
All_AIns_offset <- AllSubs_NeuralActivation$AIns_offset
All_MPFC_offset <- AllSubs_NeuralActivation$MPFC_offset

All_NAcc_ind_peak_pos <- AllSubs_NeuralActivation$NAcc_ind_peaks_pos
All_AIns_ind_peak_pos <- AllSubs_NeuralActivation$AIns_ind_peaks_pos
All_MPFC_ind_peak_pos <- AllSubs_NeuralActivation$MPFC_ind_peaks_pos

All_NAcc_ind_peak_neg <- AllSubs_NeuralActivation$NAcc_ind_peaks_neg
All_AIns_ind_peak_neg <- AllSubs_NeuralActivation$AIns_ind_peaks_neg
All_MPFC_ind_peak_neg <- AllSubs_NeuralActivation$MPFC_ind_peaks_neg

All_NAcc_tr_peak_pos <- AllSubs_NeuralActivation$NAcc_trailer_peak_pos
All_AIns_tr_peak_pos <- AllSubs_NeuralActivation$AIns_trailer_peak_pos
All_MPFC_tr_peak_pos <- AllSubs_NeuralActivation$MPFC_trailer_peak_pos

All_NAcc_tr_peak_neg <- AllSubs_NeuralActivation$NAcc_trailer_peak_neg
All_AIns_tr_peak_neg <- AllSubs_NeuralActivation$AIns_trailer_peak_neg
All_MPFC_tr_peak_neg <- AllSubs_NeuralActivation$MPFC_trailer_peak_neg
```
# Plot correlation between budget and number of theaters (M1).
```{r}
ggplot(AllSubs_NeuralActivation, aes(x = Budget, y = (All_Theaters_M1))) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor()
```
# Neuroforecasting: First month.
## M1: Aggregate data 
```{r, echo = FALSE}
FM_US_M1 <- lm(All_Gross_M1_log ~ scale(All_Theaters_M1)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M1)
r.squaredGLMM(FM_US_M1)
AIC(FM_US_M1)
```

## M2: Affect data 
```{r, echo = FALSE}
FM_US_M2 <- lm(All_Gross_M1_log ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M2)
r.squaredGLMM(FM_US_M2)
AIC(FM_US_M2)
#ggpairs(FW_US_M1_df)
```
## M3: Sequence neural signals.
```{r}
FM_US_M3 <- lm((All_Gross_M1_log) ~ 
         + scale(NAcc_onset) 
         + scale(AIns_middle)
         + scale(MPFC_offset)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M3)
r.squaredGLMM(FM_US_M3)
AIC(FM_US_M3)
```
## M4: Full model: theaters + affect + neural signals.
```{r}
FM_US_M4 <- lm((All_Gross_M1_log) ~ 
         + scale(All_Theaters_M1)
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_onset) 
         + scale(AIns_middle)
         + scale(MPFC_offset)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M4)
r.squaredGLMM(FM_US_M4)
AIC(FM_US_M4)
vif(FM_US_M4)
```
## M5: Sequence neural signals.
```{r}
FM_US_M5 <- lm((All_Gross_M1_log) ~ 
         + scale(NAcc_ISC) 
         + scale(AIns_ISC)
         + scale(MPFC_ISC)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M5)
r.squaredGLMM(FM_US_M5)
AIC(FM_US_M5)
```
## M6: Full model: theaters + affect + neural ISC
```{r}
FM_US_M6 <- lm((All_Gross_M1_log) ~ 
         + scale(All_Theaters_M1)
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ISC) 
         + scale(AIns_ISC)
         + scale(MPFC_ISC)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M6)
r.squaredGLMM(FM_US_M6)
AIC(FM_US_M6)
vif(FM_US_M6)
```
## M7: Neural positive peaks (individual).
```{r}
FM_US_M7 <- lm((All_Gross_M1_log) ~ 
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos)
         + scale(MPFC_ind_peaks_pos)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M7)
r.squaredGLMM(FM_US_M7)
AIC(FM_US_M7)
```
## M8: Full model: theaters + affect + neural ind positive peaks.
```{r}
FM_US_M8 <- lm((All_Gross_M1_log) ~ 
         + scale(All_Theaters_M1)
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos)
         + scale(MPFC_ind_peaks_pos)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M8)
r.squaredGLMM(FM_US_M8)
AIC(FM_US_M8)
vif(FM_US_M8)
```
## M9: Neural negative peaks (individual).
```{r}
FM_US_M9 <- lm((All_Gross_M1_log) ~ 
         + scale(NAcc_ind_peaks_neg) 
         + scale(AIns_ind_peaks_neg)
         + scale(MPFC_ind_peaks_neg)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M9)
r.squaredGLMM(FM_US_M9)
AIC(FM_US_M9)
```
## M10: Full model: theaters + affect + neural ind negative peaks.
```{r}
FM_US_M10 <- lm((All_Gross_M1_log) ~ 
         + scale(All_Theaters_M1)
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ind_peaks_neg) 
         + scale(AIns_ind_peaks_neg)
         + scale(MPFC_ind_peaks_neg)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M10)
r.squaredGLMM(FM_US_M10)
AIC(FM_US_M10)
vif(FM_US_M10)
```
## M11: Neural positive peaks (trailer).
```{r}
FM_US_M11 <- lm((All_Gross_M1_log) ~ 
         + scale(NAcc_trailer_peak_pos) 
         + scale(AIns_trailer_peak_pos)
         + scale(MPFC_trailer_peak_pos)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M11)
r.squaredGLMM(FM_US_M11)
AIC(FM_US_M11)
```
## M12: Full model: theaters + affect + neural trailer positive peaks.
```{r}
FM_US_M12 <- lm((All_Gross_M1_log) ~ 
         + scale(All_Theaters_M1)
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_trailer_peak_pos) 
         + scale(AIns_trailer_peak_pos)
         + scale(MPFC_trailer_peak_pos)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M12)
r.squaredGLMM(FM_US_M12)
AIC(FM_US_M12)
vif(FM_US_M12)
```
## M13: Neural negative peaks (trailer).
```{r}
FM_US_M13 <- lm((All_Gross_M1_log) ~ 
         + scale(NAcc_trailer_peak_neg) 
         + scale(AIns_trailer_peak_neg)
         + scale(MPFC_trailer_peak_neg)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M13)
r.squaredGLMM(FM_US_M13)
AIC(FM_US_M13)
```
## M14: Full model: theaters + affect + neural trailer positive peaks.
```{r}
FM_US_M14 <- lm((All_Gross_M1_log) ~ 
         + scale(All_Theaters_M1)
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_trailer_peak_neg) 
         + scale(AIns_trailer_peak_neg)
         + scale(MPFC_trailer_peak_neg)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M14)
r.squaredGLMM(FM_US_M14)
AIC(FM_US_M14)
vif(FM_US_M14)
```
# Neuroforecasting: First month controlling for number of theaters. 
## M15: affect model.
```{r}
FMT_M15 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = AllSubs_NeuralActivation )
summary(FMT_M15)
r.squaredGLMM(FMT_M15)
AIC(FMT_M15)
vif(FMT_M15)
```
## M16: Neural sequence.
```{r}
FMT_M16 <- lm((GoT_M1) ~ 
         + scale(NAcc_onset) 
         + scale(AIns_middle)
         + scale(MPFC_offset)
            , data = AllSubs_NeuralActivation )
summary(FMT_M16)
r.squaredGLMM(FMT_M16)
AIC(FMT_M16)
vif(FMT_M16)
```
## M17: Full model: affect + neural sequence.
```{r}
FMT_M17 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_onset) 
         + scale(AIns_middle)
         + scale(MPFC_offset)
            , data = AllSubs_NeuralActivation )
summary(FMT_M17)
r.squaredGLMM(FMT_M17)
AIC(FMT_M17)
vif(FMT_M17)
```
## M18: Neural ISC
```{r}
FMT_M18 <- lm((GoT_M1) ~ 
         + scale(NAcc_ISC) 
         + scale(AIns_ISC)
         + scale(MPFC_ISC)
            , data = AllSubs_NeuralActivation )
summary(FMT_M18)
r.squaredGLMM(FMT_M18)
AIC(FMT_M18)
vif(FMT_M18)
```
## M19: Full model: affect + neural ISC
```{r}
FMT_M19 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ISC) 
         + scale(AIns_ISC)
         + scale(MPFC_ISC)
            , data = AllSubs_NeuralActivation )
summary(FMT_M19)
r.squaredGLMM(FMT_M19)
AIC(FMT_M19)
vif(FMT_M19)
```
## M20: Neural individual positive peak 
```{r}
FMT_M20 <- lm((GoT_M1) ~ 
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos)
         + scale(MPFC_ind_peaks_pos)
            , data = AllSubs_NeuralActivation )
summary(FMT_M20)
r.squaredGLMM(FMT_M20)
AIC(FMT_M20)
vif(FMT_M20)
```
## M21: Full model: affect + neural individual positive peak.
```{r}
FMT_M21 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos)
         + scale(MPFC_ind_peaks_pos)
            , data = AllSubs_NeuralActivation )
summary(FMT_M21)
r.squaredGLMM(FMT_M21)
AIC(FMT_M21)
vif(FMT_M21)
```
## M22: Neural individual negative peak 
```{r}
FMT_M22 <- lm((GoT_M1) ~ 
         + scale(NAcc_ind_peaks_neg) 
         + scale(AIns_ind_peaks_neg)
         + scale(MPFC_ind_peaks_neg)
            , data = AllSubs_NeuralActivation )
summary(FMT_M22)
r.squaredGLMM(FMT_M22)
AIC(FMT_M22)
vif(FMT_M22)
```
## M23: Full model: affect + neural individual negative peak.
```{r}
FMT_M23 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ind_peaks_neg) 
         + scale(AIns_ind_peaks_neg)
         + scale(MPFC_ind_peaks_neg)
            , data = AllSubs_NeuralActivation )
summary(FMT_M23)
r.squaredGLMM(FMT_M23)
AIC(FMT_M23)
vif(FMT_M23)
```
## M24: Neural trailer positive peak 
```{r}
FMT_M24 <- lm((GoT_M1) ~ 
         + scale(NAcc_trailer_peak_pos) 
         + scale(AIns_trailer_peak_pos)
         + scale(MPFC_trailer_peak_pos)
            , data = AllSubs_NeuralActivation )
summary(FMT_M24)
r.squaredGLMM(FMT_M24)
AIC(FMT_M24)
vif(FMT_M24)
```
## M25: Full model: affect + neural trailer negative peak.
```{r}
FMT_M25 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_trailer_peak_pos) 
         + scale(AIns_trailer_peak_pos)
         + scale(MPFC_trailer_peak_pos)
            , data = AllSubs_NeuralActivation )
summary(FMT_M25)
r.squaredGLMM(FMT_M25)
AIC(FMT_M25)
vif(FMT_M25)
```
## M26: Neural trailer negative peak 
```{r}
FMT_M26 <- lm((GoT_M1) ~ 
         + scale(NAcc_trailer_peak_neg) 
         + scale(AIns_trailer_peak_neg)
         + scale(MPFC_trailer_peak_neg)
            , data = AllSubs_NeuralActivation )
summary(FMT_M26)
r.squaredGLMM(FMT_M26)
AIC(FMT_M26)
vif(FMT_M26)
```
## M27: Full model: affect + neural trailer negative peak.
```{r}
FMT_M27 <- lm((GoT_M1) ~ 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_trailer_peak_neg) 
         + scale(AIns_trailer_peak_neg)
         + scale(MPFC_trailer_peak_neg)
            , data = AllSubs_NeuralActivation )
summary(FMT_M27)
r.squaredGLMM(FMT_M27)
AIC(FMT_M27)
vif(FMT_M27)
```


```{r}
ggplot(AllSubs_NeuralActivation, aes(x = NAcc_onset, y = (GoT_total))) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor()
```

