---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
library(car)
```


```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
```

Read dataset
```{r}
AllSubs_NeuralActivation <- read.csv('/Users/luisalvarez/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuralActivation_Aggregate_Combined_Comedy_clean.csv')
```
# Create data frames for each model.
```{r}
# Define aggregate variables. 
All_Gross_W1_log <- log(AllSubs_NeuralActivation$Gross_US_W1_num)
All_Theaters_W1 <- AllSubs_NeuralActivation$Theaters_US_W1_num

All_Gross_M1_log <- log(AllSubs_NeuralActivation$Gross_US_M1)
All_Theaters_M1 <- AllSubs_NeuralActivation$Theaters_US_M1

# Define affect variables.
All_PA <- AllSubs_NeuralActivation$Pos_arousal_scaled
All_NA <- AllSubs_NeuralActivation$Neg_arousal_scaled

FW_US_M1_df <- data.frame(All_Gross_W1_log, All_Theaters_W1) 
FM_US_M14_df <- data.frame(All_Gross_M1_log, All_Theaters_M1) 
```

```{r}
# Define ISC variables. 
All_NAcc_ISC <- AllSubs_NeuralActivation$NAcc_ISC
All_AIns_ISC <- AllSubs_NeuralActivation$AIns_ISC
All_MPFC_ISC <- AllSubs_NeuralActivation$MPFC_ISC

# Define models. 
FW_US_M2_df <- data.frame(All_NAcc_ISC, All_AIns_ISC, All_MPFC_ISC) 
FW_US_M3_df <- data.frame(All_Gross_W1_log, All_PA, All_NA, All_NAcc_ISC, All_AIns_ISC, All_MPFC_ISC) 
FM_US_M16_df <- data.frame(All_Gross_M1_log, All_PA, All_NA, All_NAcc_ISC, All_AIns_ISC, All_MPFC_ISC) 

```

```{r}
# Define whole variables. 
All_NAcc_whole <- AllSubs_NeuralActivation$NAcc_whole
All_AIns_whole <- AllSubs_NeuralActivation$AIns_whole
All_MPFC_whole <- AllSubs_NeuralActivation$MPFC_whole

# Define models. 
FW_US_M4_df <- data.frame(All_NAcc_whole, All_AIns_whole, All_MPFC_whole) 
FW_US_M5_df <- data.frame(All_Gross_W1_log, All_PA, All_NA, All_NAcc_whole, All_AIns_whole, All_MPFC_whole)
FM_US_M18_df <- data.frame(All_Gross_M1_log, All_PA, All_NA, All_NAcc_whole, All_AIns_whole, All_MPFC_whole)
```

```{r}
# Define onset variables. 
All_NAcc_onset <- AllSubs_NeuralActivation$NAcc_onset
All_AIns_onset <- AllSubs_NeuralActivation$AIns_onset
All_MPFC_onset <- AllSubs_NeuralActivation$MPFC_onset

# Define models. 
FW_US_M6_df <- data.frame(All_NAcc_onset, All_AIns_onset, All_MPFC_onset) 
FW_US_M7_df <- data.frame(All_Gross_W1_log, All_PA, All_NA, All_NAcc_onset, All_AIns_onset, All_MPFC_onset)
FM_US_M20_df <- data.frame(All_Gross_M1_log, All_PA, All_NA, All_NAcc_onset, All_AIns_onset, All_MPFC_onset)
```

```{r}
# Define middle variables. 
All_NAcc_middle <- AllSubs_NeuralActivation$NAcc_middle
All_AIns_middle <- AllSubs_NeuralActivation$AIns_middle
All_MPFC_middle <- AllSubs_NeuralActivation$MPFC_middle

# Define models. 
FW_US_M8_df <- data.frame(All_NAcc_middle, All_AIns_middle, All_MPFC_middle) 
FW_US_M9_df <- data.frame(All_Gross_W1_log, All_PA, All_NA, All_NAcc_middle, All_AIns_middle, All_MPFC_middle) 
FM_US_M22_df <- data.frame(All_Gross_M1_log, All_PA, All_NA, All_NAcc_middle, All_AIns_middle, All_MPFC_middle)
```

```{r}
# Define offset variables. 
All_NAcc_offset <- AllSubs_NeuralActivation$NAcc_offset
All_AIns_offset <- AllSubs_NeuralActivation$AIns_offset
All_MPFC_offset <- AllSubs_NeuralActivation$MPFC_offset

# Define models. 
FW_US_M10_df <- data.frame(All_NAcc_offset, All_AIns_offset, All_MPFC_offset) 
FW_US_M11_df <- data.frame(All_Gross_W1_log, All_PA, All_NA, All_NAcc_offset, All_AIns_offset, All_MPFC_offset)
FM_US_M24_df <- data.frame(All_Gross_M1_log, All_PA, All_NA, All_NAcc_offset, All_AIns_offset, All_MPFC_offset)

# Seq models. 
FW_US_M12_df <- data.frame(All_NAcc_onset, All_AIns_middle, All_MPFC_offset) 
FW_US_M13_df <- data.frame(All_Gross_W1_log, All_PA, All_NA, All_NAcc_onset, All_AIns_middle, All_MPFC_offset)
FM_US_M26_df <- data.frame(All_Gross_M1_log, All_PA, All_NA, All_NAcc_onset, All_AIns_middle, All_MPFC_offset)
```


# Neuroforecasting: First Week US.
## M1: Behavioral data + Affective data
```{r, echo = FALSE}
FW_US_M1 <- lm(log(Gross_US_W1_num) ~ Theaters_US_W1_num
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
            , data = AllSubs_NeuralActivation )
summary(FW_US_M1)
r.squaredGLMM(FW_US_M1)
AIC(FW_US_M1)
ggpairs(FW_US_M1_df)
```

# FW_US_M2: ISC data alone
```{r, echo = FALSE}
FW_US_M2 <- lm(log(Gross_US_W1_num) ~  
              + Theaters_US_W1_num 
              + scale(NAcc_ISC) 
              + scale(AIns_ISC) 
              + scale(MPFC_ISC) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M2)
r.squaredGLMM(FW_US_M2)
AIC(FW_US_M2)
ggpairs(FW_US_M2_df)
```
# FW_US_M3: ISC data + affective data + behavioral data
```{r, echo = FALSE}
FW_US_M3 <- lm(log(Gross_US_W1_num) ~  
             + Theaters_US_W1_num 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_ISC) # For some reason NAcc is correlated with AIns 
             + scale(AIns_ISC) # When removing AIns, NAcc becomes sig.
             + scale(MPFC_ISC) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M3)
r.squaredGLMM(FW_US_M3)
AIC(FW_US_M3)
ggpairs(FW_US_M3_df)
```
# FW_US_M4: Whole data alone
```{r, echo = FALSE}
FW_US_M4 <- lm(log(Gross_US_W1_num) ~  
              + Theaters_US_W1_num 
              + scale(NAcc_whole) 
              + scale(AIns_whole) 
              + scale(MPFC_whole) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M4)
r.squaredGLMM(FW_US_M4)
AIC(FW_US_M4)
ggpairs(FW_US_M4_df)
```

# FW_US_M5: Whole data + affective data + behavioral data
```{r, echo = FALSE}
FW_US_M5 <- lm(log(Gross_US_W1_num) ~  
             + Theaters_US_W1_num 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_whole) 
             + scale(AIns_whole) 
             + scale(MPFC_whole) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M5)
r.squaredGLMM(FW_US_M5)
AIC(FW_US_M5)
ggpairs(FW_US_M5_df)
```

# FW_US_M6: Onset data alone
```{r, echo = FALSE}
FW_US_M6 <- lm(log(Gross_US_W1_num) ~  
              + Theaters_US_W1_num 
              + scale(NAcc_onset) 
              + scale(AIns_onset) 
              + scale(MPFC_onset) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M6)
r.squaredGLMM(FW_US_M6)
AIC(FW_US_M6)
ggpairs(FW_US_M6_df)
```

# FW_US_M7: Onset data + affective data + behavioral data
```{r, echo = FALSE}
FW_US_M7 <- lm(log(Gross_US_W1_num) ~  
             + Theaters_US_W1_num 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_onset) 
             + scale(AIns_onset) 
             + scale(MPFC_onset) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M7)
r.squaredGLMM(FW_US_M7)
AIC(FW_US_M7)
ggpairs(FW_US_M7_df)
```

# FW_US_M8: Middle data alone
```{r, echo = FALSE}
FW_US_M8 <- lm(log(Gross_US_W1_num) ~  
              + Theaters_US_W1_num 
              + scale(NAcc_middle) 
              + scale(AIns_middle) 
              + scale(MPFC_middle) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M8)
r.squaredGLMM(FW_US_M8)
AIC(FW_US_M8)
ggpairs(FW_US_M8_df)
```

# FW_US_M9: Middle data + affective data + behavioral data
```{r, echo = FALSE}
FW_US_M9 <- lm(log(Gross_US_W1_num) ~  
             + Theaters_US_W1_num 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_middle) 
             + scale(AIns_middle) 
             + scale(MPFC_middle) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M9)
r.squaredGLMM(FW_US_M9)
AIC(FW_US_M9)
ggpairs(FW_US_M9_df)
```

# FW_US_M10: Offset data alone
```{r, echo = FALSE}
FW_US_M10 <- lm(log(Gross_US_W1_num) ~  
              + Theaters_US_W1_num 
              + scale(NAcc_offset) 
              + scale(AIns_offset) 
              + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M10)
r.squaredGLMM(FW_US_M10)
AIC(FW_US_M10)
ggpairs(FW_US_M10_df)
```

# FW_US_M11: Onset data + affective data + behavioral data
```{r, echo = FALSE}
FW_US_M11 <- lm(log(Gross_US_W1_num) ~  
             + Theaters_US_W1_num 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_offset) 
             + scale(AIns_offset) 
             + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M11)
r.squaredGLMM(FW_US_M11)
AIC(FW_US_M11)
ggpairs(FW_US_M11_df)
```

# FW_US_M12: Seq data alone
```{r, echo = FALSE}
FW_US_M12 <- lm(log(Gross_US_W1_num) ~  
              + Theaters_US_W1_num 
              + scale(NAcc_onset) 
              + scale(AIns_middle) 
              + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M12)
r.squaredGLMM(FW_US_M12)
AIC(FW_US_M12)
ggpairs(FW_US_M12_df)
```

# FW_US_M13: Seq data + affective data + behavioral data
```{r, echo = FALSE}
FW_US_M13 <- lm(log(Gross_US_W1_num) ~  
             + Theaters_US_W1_num 
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_onset) 
             + scale(AIns_middle) 
             + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FW_US_M13)
r.squaredGLMM(FW_US_M13)
AIC(FW_US_M13)
ggpairs(FW_US_M13_df)
```
# Neuroforecasting: First Month US.

## FM_US_M14: Behavioral data + affective data
```{r, echo = FALSE}
FM_US_M14 <- lm(log(Gross_US_M1) ~  
         + Theaters_US_M1 
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         #+ scale(W_score_scaled)
            , data = AllSubs_NeuralActivation )
summary(FM_US_M14)
r.squaredGLMM(FM_US_M14)
AIC(FM_US_M14)
ggpairs(FM_US_M14_df)
```

# FM_US_M15: ISC data alone
```{r, echo = FALSE}
FM_US_M15 <- lm(log(Gross_US_M1) ~  
              + Theaters_US_M1
              + scale(NAcc_ISC) 
              + scale(AIns_ISC) 
              + scale(MPFC_ISC) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M15)
r.squaredGLMM(FM_US_M15)
AIC(FM_US_M15)
```

# FM_US_M16: ISC data + affective data + behavioral data
```{r, echo = FALSE}
FM_US_M16 <- lm(log(Gross_US_M1) ~  
             + Theaters_US_M1
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_ISC) 
             + scale(AIns_ISC) 
             + scale(MPFC_ISC) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M16)
r.squaredGLMM(FM_US_M16)
AIC(FM_US_M16)
ggpairs(FM_US_M16_df)
```
# FM_US_M17: Whole data alone
```{r, echo = FALSE}
FM_US_M17 <- lm(log(Gross_US_M1) ~  
              + Theaters_US_M1
              + scale(NAcc_whole) 
              + scale(AIns_whole) 
              + scale(MPFC_whole) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M17)
r.squaredGLMM(FM_US_M17)
AIC(FM_US_M17)
```

# FM_US_M18: Whole data + affective data + behavioral data
```{r, echo = FALSE}
FM_US_M18 <- lm(log(Gross_US_M1) ~  
             + Theaters_US_M1
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_whole) 
             + scale(AIns_whole) 
             + scale(MPFC_whole) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M18)
r.squaredGLMM(FM_US_M18)
AIC(FM_US_M18)
ggpairs(FM_US_M18_df)
```

# FM_US_M19: Onset data alone
```{r, echo = FALSE}
FM_US_M19 <- lm(log(Gross_US_M1) ~  
              + Theaters_US_M1
              + scale(NAcc_onset) 
              + scale(AIns_onset) 
              + scale(MPFC_onset) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M19)
r.squaredGLMM(FM_US_M19)
AIC(FM_US_M19)
```

# FM_US_M20: Onset data + affective data + behavioral data
```{r, echo = FALSE}
FM_US_M20 <- lm(log(Gross_US_M1) ~  
             + Theaters_US_M1
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_onset) 
             + scale(AIns_onset) 
             + scale(MPFC_onset) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M20)
r.squaredGLMM(FM_US_M20)
AIC(FM_US_M20)
ggpairs(FM_US_M20_df)
```

# FM_US_M17: Middle data alone
```{r, echo = FALSE}
FM_US_M21 <- lm(log(Gross_US_M1) ~  
              + Theaters_US_M1
              + scale(NAcc_middle) 
              + scale(AIns_middle) 
              + scale(MPFC_middle) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M21)
r.squaredGLMM(FM_US_M21)
AIC(FM_US_M21)
```

# FM_US_M22: Middle data + affective data + behavioral data
```{r, echo = FALSE}
FM_US_M22 <- lm(log(Gross_US_M1) ~  
             + Theaters_US_M1
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_middle) 
             + scale(AIns_middle) 
             + scale(MPFC_middle) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M22)
r.squaredGLMM(FM_US_M22)
AIC(FM_US_M22)
ggpairs(FM_US_M22_df)
```

# FM_US_M23: Offset data alone
```{r, echo = FALSE}
FM_US_M23 <- lm(log(Gross_US_M1) ~  
              + Theaters_US_M1
              + scale(NAcc_offset) 
              + scale(AIns_offset) 
              + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M23)
r.squaredGLMM(FM_US_M23)
AIC(FM_US_M23)
```

# FM_US_M24: Offset data + affective data + behavioral data
```{r, echo = FALSE}
FM_US_M24 <- lm(log(Gross_US_M1) ~  
             + Theaters_US_M1
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_offset) 
             + scale(AIns_offset) 
             + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M24)
r.squaredGLMM(FM_US_M24)
AIC(FM_US_M24)
ggpairs(FM_US_M24_df)
```

# FM_US_M25: Seq data alone
```{r, echo = FALSE}
FM_US_M25 <- lm(log(Gross_US_M1) ~  
              + Theaters_US_M1
              + scale(NAcc_onset) 
              + scale(AIns_middle) 
              + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M25)
r.squaredGLMM(FM_US_M25)
AIC(FM_US_M25)
```

# FM_US_M26: Sqe data + affective data + behavioral data
```{r, echo = FALSE}
FM_US_M26 <- lm(log(Gross_US_M1) ~  
             + Theaters_US_M1 
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_onset) 
             + scale(AIns_middle) 
             + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(FM_US_M26)
r.squaredGLMM(FM_US_M26)
AIC(FM_US_M26)
ggpairs(FM_US_M26_df)
```
# Total_US_M27: Seq data + affective data + behavioral data
```{r, echo = FALSE}
Total_US_M27 <- lm(log(Gross_Total_US) ~  
             + Total_Theaters_US 
             #+ Total_weeks 
             #+ Weeks_avg_per_theater
             + scale(Pos_arousal_scaled) 
             + scale(Neg_arousal_scaled)  
             #+ scale(W_score_scaled) 
             + scale(NAcc_onset) 
             + scale(AIns_middle) 
             + scale(MPFC_offset) 
            , data = AllSubs_NeuralActivation)
summary(Total_US_M27)
r.squaredGLMM(Total_US_M27)
AIC(Total_US_M27)

```




