---
title: "RM Thesis: Individual & Aggregate Choice Analysis."
author: "Luis A."
date: "2024-05-07"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Loading libraries
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(ggpubr)
library(GGally)
library(car)
library(tidyverse)
library(lme4)
library(lmerTest)
library("MuMIn")
library(lmtest)
library(boot)
library(modelsummary)
library(pandoc)
library(tinytable)
library(cowplot)
library(sjPlot)
library(patchwork)
library(magick)
library(ppcor)
```


```{r, echo=FALSE}

Individual_BothTrailers_df <- read.csv('/Users/la/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuroTS_GLM_ISC.csv') %>% mutate(Type = factor(Type, levels = c("Comedy", "Horror")))

Aggregate_BothTrailers_df <- read.csv('/Users/la/Documents/GitHub/RM_Thesis_Neuroforecasting/ProcessedData/AllSubs_NeuroTS_GLM_ISC_AGG.csv') %>% mutate(Type = factor(Type, levels = c("comedy", "horror")))

```

# Invididual Choice.

## Preference per genre.
```{r}

Ind_Genre_preference <- Individual_BothTrailers_df %>% group_by(Type) %>% 
  summarise(Mean_W=mean(W_score), SD_W=sd(W_score), 
            Mean_W_scaled=mean(W_score_scaled), SD_W_score_scaled=sd(W_score_scaled))

Ind_Comedy_df <- filter(Individual_BothTrailers_df, Type=="Comedy")
Ind_Horror_df <- filter(Individual_BothTrailers_df, Type=="Horror")

# Perform the paired sample t-test ->. Can't do, samples are unequal.
#t_test_result <- t.test(Ind_Comedy_df$W_score, Ind_Horror_df$W_score,, paired = TRUE)
genre_model <- lmer(W_score ~ Type + (1 | Participant), data = Individual_BothTrailers_df)

Ind_Genre_preference
summary(genre_model)
print(contrasts(Individual_BothTrailers_df$Type))
```


## IndBoth: Fixed time series models.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

contrasts(Individual_BothTrailers_df$Type) <- rbind(1, -1)
colnames(contrasts(Individual_BothTrailers_df$Type)) <- levels(Individual_BothTrailers_df$Type)[2]

# Create affect only model. 
IndBoth_Affect <- lmer(scale(W_score) ~ 
                        Type +
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create neuro sequence only model.
IndBoth_SeqNeuro <- lmer(scale(W_score) ~
                        Type +   
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        Type:scale(NAcc_seg2) + 
                        Type:scale(AIns_seg3) + 
                        Type:scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and neuro sequence model.
IndBoth_Affect_and_SeqNeuro <- lmer(scale(W_score) ~
                        Type +              
                        scale(Pos_arousal_scaled) +
                        scale(Neg_arousal_scaled) +
                        scale(NAcc_seg2) + 
                        scale(AIns_seg3) + 
                        scale(MPFC_seg5) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_seg2) +
                        Type:scale(AIns_seg3) +
                        Type*scale(MPFC_seg5) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

#summary(IndBoth_Affect_and_SeqNeuro) 
# Create list with all models.
IndBoth_Seq_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro seq" = IndBoth_SeqNeuro, 
  "Affect & Neuro seq" = IndBoth_Affect_and_SeqNeuro)

# Make table with all models. 
IndBoth_Seq_models <- modelsummary(IndBoth_Seq_list, stars=TRUE, 
                           #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #estimate  = "{estimate} ({std.error}) {stars}",
                           estimate = c("b={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}"),
                           statistic = NULL,
                           #output = "html",
                           #output="Thesis_LMM_Outputs/Thesis_FMRIP_Ind_FixedTimeSeries.docx", 
                           output = "dataframe",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") %>% dplyr::select(-part, -statistic)


print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_Seq_models
```

# Trailer preference and affect ratings pairplot.
```{r}
ggpairs(Individual_BothTrailers_df[, c("Type", "W_score_scaled", "Pos_arousal_scaled", "Neg_arousal_scaled")], columns = 2:ncol(Individual_BothTrailers_df[, c("Type", "W_score_scaled", "Pos_arousal_scaled", "Neg_arousal_scaled")]), 
        aes(color = Type)) 
```


```{r, echo=FALSE}
#ggpairs(IndBoth_Affect_and_SeqNeuro[, c("Type", "W_score_scaled", "Pos_arousal_scaled", "Neg_arousal_scaled", "NAcc_seg2", "AIns_seg3", "MPFC_seg5")], columns = 2:ncol(IndBoth_Affect_and_SeqNeuro[, c("Type", "W_score_scaled", "Pos_arousal_scaled", "Neg_arousal_scaled", "NAcc_seg2", "AIns_seg3", "MPFC_seg5")]), 
#        aes(color = Type)) 

```

## IndBoth: Modal peak models.
```{r, echo=FALSE, warning=FALSE, message=FALSE}

IndBoth_MPNeuro <- lmer(scale(W_score) ~
                        Type +   
                        scale(NAcc_DP2) +
                        scale(AIns_DP2) +
                        scale(MPFC_DP2) +
                        Type:scale(NAcc_DP2) + 
                        Type:scale(AIns_DP2) + 
                        Type:scale(MPFC_DP2) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and neuro sequence model.
IndBoth_Affect_and_MPNeuro <- lmer(scale(W_score) ~
                        Type +              
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_DP2) +
                        scale(AIns_DP2) +
                        scale(MPFC_DP2) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_DP2) + 
                        Type:scale(AIns_DP2) + 
                        Type:scale(MPFC_DP2) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df)

# Create list with all models.
IndBoth_MP_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro seq" = IndBoth_MPNeuro, 
  "Affect & Neuro seq" = IndBoth_Affect_and_MPNeuro)

# Make table with all models. 
IndBoth_MP_models <- modelsummary(IndBoth_MP_list, stars=TRUE, 
                           #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #estimate  = "{estimate} ({std.error}) {stars}",
                           estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                           statistic = NULL,
                           #output = "html",
                           output = "dataframe",
                           #output="Thesis_LMM_Outputs/Thesis_FMRIP_Ind_ModalPeak.docx", 
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") %>% dplyr::select(-part, -statistic)

print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_MP_models
```
### What is AIns modal peak capturing? 
```{r}
# AIns modal peak is slightly correlated with arousal, but barely. 

Individual_BothTrailers_Horror_df <- filter(Individual_BothTrailers_df, Type=="Horror")

ggpairs(Individual_BothTrailers_df[, c("Type", "W_score", "Pos_arousal_scaled", "Neg_arousal_scaled", "A_score", "F_score", "AIns_DP1", "AIns_DP2", "NAcc_DP2", "MPFC_DP2")], columns = 2:ncol(Individual_BothTrailers_df[, c("Type", "W_score", "Pos_arousal_scaled", "Neg_arousal_scaled", "A_score", "F_score", "AIns_DP1", "AIns_DP2", "NAcc_DP2", "MPFC_DP2")]), 
        aes(color = Type)) 


```


# IndBoth: Peak models
```{r}

Individual_BothTrailers_IP <- filter(Individual_BothTrailers_df, 
                                     NAcc_ind_peaks_pos>0.5, 
                                     AIns_ind_peaks_pos>0.5,
                                     MPFC_ind_peaks_pos>0.5)

IndBoth_PNeuro <- lmer(scale(W_score) ~
                        Type +   
                        scale(NAcc_IP) +
                        scale(AIns_IP) +
                        scale(MPFC_IP) +
                        Type:scale(NAcc_IP) + 
                        Type:scale(AIns_IP) + 
                        Type:scale(MPFC_IP) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and neuro sequence model.
IndBoth_Affect_and_PNeuro <- lmer(scale(W_score) ~
                        Type +              
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_IP) +
                        scale(AIns_IP) +
                        scale(MPFC_IP) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_IP) + 
                        Type:scale(AIns_IP) + 
                        Type:scale(MPFC_IP) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df)

# Create list with all models.
IndBoth_P_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro IP" = IndBoth_PNeuro, 
  "Affect & Neuro IP" = IndBoth_Affect_and_PNeuro)

# Make table with all models. 
IndBoth_P_models <- modelsummary(IndBoth_P_list, stars=TRUE, 
                           #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #estimate  = "{estimate} ({std.error}){stars}",
                           estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                           statistic = NULL,
                           #output = "html",
                           output = "dataframe",
                           #output="Thesis_LMM_Outputs/Thesis_FMRIP_Ind_IndPeak.docx", 
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") %>% dplyr::select(-part, -statistic)

print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_P_models
```

```{r}
ggpairs(Individual_BothTrailers_df[, c("Type", "W_score", "NAcc_IP", "AIns_IP", "MPFC_IP")], columns = 2:ncol(Individual_BothTrailers_df[, c("Type", "W_score", "NAcc_IP", "AIns_IP", "MPFC_IP")]), aes(color = Type)) 


```


## IndBoth: GLM whole models.
```{r}
# Create GLM whole model (only including neural data).
IndBoth_GLMw_Neuro <- lmer(scale(W_score) ~
                        Type +   
                        scale(NAcc_GLM_long) +
                        scale(AIns_GLM_long) +
                        scale(vmPFC_GLM_long) +
                        Type:scale(NAcc_GLM_long) + 
                        Type:scale(AIns_GLM_long) + 
                        Type:scale(vmPFC_GLM_long) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and GLM whole model.
IndBoth_Affect_and_GLMw <- lmer(scale(W_score) ~
                        Type +              
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_GLM_long) +
                        scale(AIns_GLM_long) +
                        scale(vmPFC_GLM_long) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_GLM_long) + 
                        Type:scale(AIns_GLM_long) + 
                        Type:scale(vmPFC_GLM_long) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df)

# Create list with all models.
IndBoth_GLMw_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro GLM whole" = IndBoth_GLMw_Neuro, 
  "Affect & GLM whole" = IndBoth_Affect_and_GLMw)

# Make table with all models. 
IndBoth_GLMw_models <- modelsummary(IndBoth_GLMw_list, stars=TRUE, 
                           #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #estimate  = "{estimate} ({std.error}) {stars}",
                           estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                           statistic = NULL,
                           #output = "html",
                           output = "dataframe",
                           #output="Thesis_LMM_Outputs/Thesis_FMRIP_Ind_GLM_whole.docx", 
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") %>% dplyr::select(-part, -statistic)

print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_GLMw_models
```

## IndBoth: GLM onset models.
```{r}
# Create GLM onset model (only including neural data).
IndBoth_GLMo_Neuro <- lmer(scale(W_score) ~
                        Type +   
                        scale(NAcc_GLM_seg1) +
                        scale(AIns_GLM_seg1) +
                        scale(vmPFC_GLM_seg1) +
                        Type:scale(NAcc_GLM_seg1) + 
                        Type:scale(AIns_GLM_seg1) + 
                        Type:scale(vmPFC_GLM_seg1) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and GLM onset model.
IndBoth_Affect_and_GLMo <- lmer(scale(W_score) ~
                        Type +              
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_GLM_seg1) +
                        scale(AIns_GLM_seg1) +
                        scale(vmPFC_GLM_seg1) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                         Type:scale(NAcc_GLM_seg1) + 
                        Type:scale(AIns_GLM_seg1) + 
                        Type:scale(vmPFC_GLM_seg1) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df)

# Create list with all models.
IndBoth_GLMo_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro GLM onset" = IndBoth_GLMo_Neuro, 
  "Affect & GLM onset" = IndBoth_Affect_and_GLMo)

# Make table with all models. 
IndBoth_GLMo_models <- modelsummary(IndBoth_GLMo_list, stars=TRUE, 
                           #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #estimate  = "{estimate} ({std.error}) {stars}",
                           estimate = c("ß={estimate}, t = {statistic}, s.e. = {std.error}, p-val = {p.value}"),
                           statistic = NULL,
                           #output = "html",
                           output = "dataframe",
                           #output="Thesis_LMM_Outputs/Thesis_FMRIP_Ind_GLM_onset.docx", 
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") %>% dplyr::select(-part, -statistic)

print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_GLMo_models
```

## IndBoth: Inter-subject correlation (ISC) models.
```{r}
# Create ISC model (only including neural data).
IndBoth_ISC_Neuro <- lmer(scale(W_score) ~
                        Type +   
                        scale(NAcc_ISC) +
                        scale(AIns_ISC) +
                        scale(MPFC_ISC) +
                        Type:scale(NAcc_ISC) + 
                        Type:scale(AIns_ISC) + 
                        Type:scale(MPFC_ISC) +
                        (1|Participant) + (1|Trailer), 
                        data = Individual_BothTrailers_df) 

# Create affect and ISC model.
IndBoth_Affect_and_ISC <- lmer(scale(W_score) ~
                        Type +              
                        scale(Pos_arousal_scaled) + 
                        scale(Neg_arousal_scaled) + 
                        scale(NAcc_ISC) +
                        scale(AIns_ISC) +
                        scale(MPFC_ISC) +
                        Type:scale(Pos_arousal_scaled) +
                        Type:scale(Neg_arousal_scaled) +
                        Type:scale(NAcc_ISC) + 
                        Type:scale(AIns_ISC) + 
                        Type:scale(MPFC_ISC) +
                        (1 | Participant) + (1 | Trailer), 
                        data = Individual_BothTrailers_df)


# Create list with all models.
IndBoth_ISC_list <- list(
  "Affect" = IndBoth_Affect, 
  "Neuro ISC" = IndBoth_ISC_Neuro, 
  "Affect & ISC" = IndBoth_Affect_and_ISC)

# Make table with all models. 
IndBoth_ISC_models <- modelsummary(IndBoth_ISC_list, stars=TRUE, 
                           #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                           #estimate  = "{estimate} ({std.error}) {stars}",
                           estimate = c("ß={estimate}, t = {statistic}, s.e. = {std.error}, p-val = {p.value}"),
                           statistic = NULL,
                           #output = "html",
                           output = "dataframe",
                           #output="Thesis_LMM_Outputs/Thesis_FMRIP_Ind_ISC.docx",
                           gof_omit="F|RMSE|Log|Num.Obs.|SD (Observations)") %>% dplyr::select(-part, -statistic)

print(contrasts(Individual_BothTrailers_df$Type))
IndBoth_ISC_models
```


# Aggregate Results Both Trailers. 

### What is the correlation between Positive arousal and Watch choice at the aggregate level?
```{r}

Agg_PA_W_corr <- cor.test(Aggregate_BothTrailers_df$Pos_arousal_scaled, Aggregate_BothTrailers_df$W_score, method = "pearson")

print("At the aggregate level, positive arousal and w_score have the following correlation: ")
Agg_PA_W_corr

```


## AggBoth: Seq Models.
```{r, echo=FALSE}
Aggregate_BothTrailers_df <- mutate(Aggregate_BothTrailers_df, Type = factor(Type, levels = c("comedy", "horror")))
contrasts(Aggregate_BothTrailers_df$Type) <- rbind(1, -1)
colnames(contrasts(Aggregate_BothTrailers_df$Type)) <- levels(Aggregate_BothTrailers_df$Type)[2]

# Create aggregate model for first month gross (log).
AggBoth_Affect_M1 <-lm(log(Gross_M1_updated) ~ 
         + Type                      
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
            , data = Aggregate_BothTrailers_df)

AggBoth_Choice_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(W_score) 
         + Type:scale(W_score)  
            , data = Aggregate_BothTrailers_df)

AggBoth_Seq_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(NAcc_seg1) 
         #+ scale(AIns_seg3)
         #+ scale(MPFC_seg5)
         + Type:scale(NAcc_seg1)
         #+ Type:scale(AIns_seg3)
         #+ Type:scale(MPFC_seg5)
            , data = Aggregate_BothTrailers_df)

AggBoth_SeqAffect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_seg1) 
         #+ scale(AIns_seg3)
         #+ scale(MPFC_seg5)
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_seg1)
         #+ Type:scale(AIns_seg3)
         #+ Type:scale(MPFC_seg5)
            , data = Aggregate_BothTrailers_df) 


AggBoth_ChoiceSeq_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(W_score) 
         + scale(NAcc_seg1) 
         #+ scale(AIns_seg3)
         #+ scale(MPFC_seg5)
         + Type:scale(W_score) 
         + Type:scale(NAcc_seg1)
         #+ Type:scale(AIns_seg3)
         #+ Type:scale(MPFC_seg5)
            , data = Aggregate_BothTrailers_df) 

AggBoth_Seq_list = list(
  #"Affect GM1" = AggBoth_Affect_M1, 
  "Choice GM1" = AggBoth_Choice_M1,
  "Neuro Seq GM1" = AggBoth_Seq_M1,
  #"Affect Neuro Seq GM1" = AggBoth_SeqAffect_M1,
  "Choice Neuro Seq GM1" = AggBoth_ChoiceSeq_M1)

AggBoth_Seq_models <- modelsummary(AggBoth_Seq_list, stars=TRUE, 
                               #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #estimate  = "{estimate} ({std.error}) {stars}",
                               estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                               statistic = NULL,
                               output="dataframe",
                               #output="html",
                               #output="Thesis_LMM_Outputs/Thesis_FMRIP_Agg_FixedTimeSeries.docx",
                               gof_omit = "F|RMSE|Log") %>% dplyr::select(-part, -statistic)

print(contrasts(Aggregate_BothTrailers_df$Type))
AggBoth_Seq_models

```

```{r}
ggpairs(Aggregate_BothTrailers_df[, c("Type", "Gross_M1_updated_log", "W_score", "Pos_arousal_scaled", "Neg_arousal_scaled")], columns = 2:ncol(Aggregate_BothTrailers_df[, c("Type", "Gross_M1_updated_log", "W_score", "Pos_arousal_scaled", "Neg_arousal_scaled")]), 
        aes(color = Type)) 
```


```{r, echo=FALSE}
ggplot(Aggregate_BothTrailers_df, aes(x = (NAcc_DP2), y = log(Gross_M1_updated), color=Type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_cor() +
  geom_text(aes(label = Trailer), vjust = 2)
```

## AggBoth: Individual Peak (IP) Models.
```{r}

AggBoth_IP_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos) 
         + scale(MPFC_ind_peaks_pos) 
         + Type:scale(NAcc_ind_peaks_pos) 
         + Type:scale(AIns_ind_peaks_pos)
         + Type:scale(MPFC_ind_peaks_pos)
            , data = Aggregate_BothTrailers_df )

AggBoth_IP_Affect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos) 
         + scale(MPFC_ind_peaks_pos) 
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_ind_peaks_pos) 
         + Type:scale(AIns_ind_peaks_pos)
         + Type:scale(MPFC_ind_peaks_pos)
            , data = Aggregate_BothTrailers_df)

AggBoth_IP_Choice_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(W_score) 
         + scale(NAcc_ind_peaks_pos) 
         + scale(AIns_ind_peaks_pos) 
         + scale(MPFC_ind_peaks_pos) 
         + Type:scale(W_score) 
         + Type:scale(NAcc_ind_peaks_pos) 
         + Type:scale(AIns_ind_peaks_pos)
         + Type:scale(MPFC_ind_peaks_pos)
            , data = Aggregate_BothTrailers_df) 

AggBoth_IP_list = list(
  #"Affect GM1" = AggBoth_Affect_M1, 
  "Choice GM1" = AggBoth_Choice_M1,
  "Neuro MP GM1" = AggBoth_IP_M1,
  #"Affect Neuro IP" = AggBoth_MPAffect_M1,
  "Choice Neuro IP" = AggBoth_IP_Choice_M1)

AggBoth_IP_models <- modelsummary(AggBoth_IP_list, stars=TRUE, 
                               #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #statistic = c("({std.error})"),
                               #estimate  = "{estimate} ({std.error}){stars}",
                               estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                               statistic = NULL,
                               output="dataframe",
                               #output="html",
                               #output="Thesis_LMM_Outputs/Thesis_FMRIP_Agg_IndPeak.docx",
                               gof_omit = "F|RMSE|Log") %>% dplyr::select(-part, -statistic)

print(contrasts(Aggregate_BothTrailers_df$Type))
AggBoth_IP_models


```




## AggBoth: Modal Peak (MP) Models.
```{r, echo=FALSE}

Aggregate_BothTrailers_df <- mutate(Aggregate_BothTrailers_df, Type = factor(Type, levels = c("horror", "comedy")))
contrasts(Aggregate_BothTrailers_df$Type) <- rbind(-1, 1)
colnames(contrasts(Aggregate_BothTrailers_df$Type)) <- levels(Aggregate_BothTrailers_df$Type)[2]

AggBoth_Affect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                      
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
            , data = Aggregate_BothTrailers_df)

AggBoth_Choice_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(W_score) 
         + Type:scale(W_score)  
            , data = Aggregate_BothTrailers_df)

AggBoth_MP_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(NAcc_DP2) 
         + scale(AIns_DP2) 
         + scale(MPFC_DP2) 
         + Type:scale(NAcc_DP2) 
         + Type:scale(AIns_DP2)
         + Type:scale(MPFC_DP2)
            , data = Aggregate_BothTrailers_df )

AggBoth_MPAffect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_DP2) 
         + scale(AIns_DP2) 
         + scale(MPFC_DP2) 
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_DP2) 
         + Type:scale(AIns_DP2)
         + Type:scale(MPFC_DP2)
            , data = Aggregate_BothTrailers_df)

AggBoth_ChoiceMPA_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(W_score) 
         + scale(NAcc_DP2) 
         + scale(AIns_DP2) 
         + scale(MPFC_DP2) 
         + Type:scale(W_score) 
         + Type:scale(NAcc_DP2) 
         + Type:scale(AIns_DP2)
         + Type:scale(MPFC_DP2)
            , data = Aggregate_BothTrailers_df) 

AggBoth_MP_list = list(
  #"Affect GM1" = AggBoth_Affect_M1, 
  "Choice GM1" = AggBoth_Choice_M1,
  "Neuro MP GM1" = AggBoth_MP_M1,
  #"Affect Neuro MP GM1" = AggBoth_MPAffect_M1,
  "Choice Neuro MP GM1" = AggBoth_ChoiceMPA_M1)

AggBoth_MP_models <- modelsummary(AggBoth_MP_list, stars=TRUE, 
                               #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #statistic = c("({std.error})"),
                               #estimate  = "{estimate} ({std.error}) {stars}",
                               estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                               statistic = NULL,
                               output="dataframe",
                               #output="html",
                               #output="Thesis_LMM_Outputs/Thesis_FMRIP_Agg_ModalPeak.docx",
                               gof_omit = "F|RMSE|Log") %>% dplyr::select(-part, -statistic)

print(contrasts(Aggregate_BothTrailers_df$Type))
AggBoth_MP_models
vif(AggBoth_ChoiceMPA_M1, type="predictor")

```



```{r}
ggpairs(Aggregate_BothTrailers_df[, c("Type", "Gross_M1_updated_log", "W_score",  "NAcc_DP2", "AIns_DP2", "MPFC_DP2")], columns = 2:ncol(Aggregate_BothTrailers_df[, c("Type", "Gross_M1_updated_log", "W_score", "NAcc_DP2", "AIns_DP2", "MPFC_DP2")]), 
        aes(color = Type)) 
```


## AggBoth: GLM whole models.
```{r}

AggBoth_GLMw_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(NAcc_GLM_long) 
         + scale(AIns_GLM_long) 
         + scale(vmPFC_GLM_long) 
         + Type:scale(NAcc_GLM_long) 
         + Type:scale(AIns_GLM_long)
         + Type:scale(vmPFC_GLM_long)
            , data = Aggregate_BothTrailers_df )
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_GLMw_Affect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_GLM_long) 
         + scale(AIns_GLM_long) 
         + scale(vmPFC_GLM_long) 
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_GLM_long) 
         + Type:scale(AIns_GLM_long)
         + Type:scale(vmPFC_GLM_long)
            , data = Aggregate_BothTrailers_df)
          #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_GLMw_Choice_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(W_score) 
         + scale(NAcc_GLM_long) 
         + scale(AIns_GLM_long) 
         + scale(vmPFC_GLM_long) 
         + Type:scale(W_score) 
         + Type:scale(NAcc_GLM_long) 
         + Type:scale(AIns_GLM_long)
         + Type:scale(vmPFC_GLM_long)
            , data = Aggregate_BothTrailers_df) 
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_GLMw_list = list(
  #"Affect M1" = AggBoth_Affect_M1, 
  "Choice M1" = AggBoth_Choice_M1,
  "GLM whole" = AggBoth_GLMw_M1,
  #"Affect Neuro MP GM1" = AggBoth_MPAffect_M1,
  "Choice & GLM whole" = AggBoth_GLMw_Choice_M1)

AggBoth_GLMw_models <- modelsummary(AggBoth_GLMw_list, stars=TRUE, 
                               #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #statistic = c("({std.error})"),
                               #statistic = c("({std.error})"),
                               estimate  = "{estimate} ({std.error}) {stars}",
                               statistic = NULL,
                               output="dataframe",
                               #output="html",
                               #output="Thesis_LMM_Outputs/Thesis_FMRIP_Agg_GLM_whole.docx",
                               gof_omit = "F|RMSE|Log") #%>% dplyr::select(-part, -statistic)


```


## AggBoth: GLM onset models.
```{r}
AggBoth_GLMo_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(NAcc_GLM_seg1) 
         + scale(AIns_GLM_seg1) 
         + scale(vmPFC_GLM_seg1) 
         + Type:scale(NAcc_GLM_seg1) 
         + Type:scale(AIns_GLM_seg1)
         + Type:scale(vmPFC_GLM_seg1)
            , data = Aggregate_BothTrailers_df )
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_GLMo_Affect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_GLM_seg1) 
         + scale(AIns_GLM_seg1) 
         + scale(vmPFC_GLM_seg1) 
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_GLM_seg1) 
         + Type:scale(AIns_GLM_seg1)
         + Type:scale(vmPFC_GLM_seg1)
            , data = Aggregate_BothTrailers_df)
          #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_GLMo_Choice_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(W_score) 
         + scale(NAcc_GLM_seg1) 
         + scale(AIns_GLM_seg1) 
         + scale(vmPFC_GLM_seg1) 
         + Type:scale(W_score) 
         + Type:scale(NAcc_GLM_seg1) 
         + Type:scale(AIns_GLM_seg1)
         + Type:scale(vmPFC_GLM_seg1)
            , data = Aggregate_BothTrailers_df) 
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_GLMo_list = list(
  #"Affect M1" = AggBoth_Affect_M1, 
  "Choice M1" = AggBoth_Choice_M1,
  "GLM onset" = AggBoth_GLMo_M1,
  #"Affect & GLM onset" = AggBoth_MPAffect_M1,
  "Choice & GLM onset" = AggBoth_GLMo_Choice_M1)

AggBoth_GLMo_models <- modelsummary(AggBoth_GLMo_list, stars=TRUE, 
                               #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #statistic = c("({std.error})"),
                               #statistic = c("({std.error})"),
                               estimate  = "{estimate} ({std.error}){stars}",
                               statistic = NULL,
                               output="dataframe",
                               #output="html",
                               #output="Thesis_LMM_Outputs/Thesis_FMRIP_Agg_GLM_onset.docx",
                               gof_omit = "F|RMSE|Log") %>% dplyr::select(-part, -statistic)

AggBoth_GLMo_models
```

## AggBoth: Inter-subject correlation.
```{r}

AggBoth_ISC_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type
         + scale(NAcc_ISC) 
         + scale(AIns_ISC) 
         + scale(MPFC_ISC) 
         + Type:scale(NAcc_ISC) 
         + Type:scale(AIns_ISC)
         + Type:scale(MPFC_ISC)
            , data = Aggregate_BothTrailers_df )
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_ISC_Affect_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(Pos_arousal_scaled) 
         + scale(Neg_arousal_scaled)
         + scale(NAcc_ISC) 
         + scale(AIns_ISC) 
         + scale(MPFC_ISC) 
         + Type:scale(Pos_arousal_scaled) 
         + Type:scale(Neg_arousal_scaled)
         + Type:scale(NAcc_ISC) 
         + Type:scale(AIns_ISC)
         + Type:scale(MPFC_ISC)
            , data = Aggregate_BothTrailers_df)
          #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_ISC_Choice_M1 <- lm(log(Gross_M1_updated) ~ 
         + Type                        
         + scale(W_score) 
         + scale(NAcc_ISC) 
         + scale(AIns_ISC) 
         + scale(MPFC_ISC) 
         + Type:scale(W_score) 
         + Type:scale(NAcc_ISC) 
         + Type:scale(AIns_ISC)
         + Type:scale(MPFC_ISC)
            , data = Aggregate_BothTrailers_df) 
         #%>% mutate(Type = factor(Type, levels = c("comedy", "horror"))))

AggBoth_ISC_list = list(
  #"Affect M1" = AggBoth_Affect_M1, 
  "Choice M1" = AggBoth_Choice_M1,
  "ISC" = AggBoth_ISC_M1,
  #"Affect & ISC" = AggBoth_ISC_Affect_M1,
  "Choice & ISC" = AggBoth_ISC_Choice_M1)

AggBoth_ISC_models <- modelsummary(AggBoth_ISC_list, stars=TRUE, 
                               #statistic = c("t = {statistic}", "s.e. = {std.error}, p-val = {p.value}"),
                               #statistic = c("({std.error})"),
                               #statistic = c("({std.error})"),
                               #estimate  = "{estimate} ({std.error}){stars}",
                               estimate = c("ß={estimate}; t={statistic}; s.e.={std.error}; p-val={p.value}{stars}"),
                               statistic = NULL,
                               output="dataframe",
                               #output="html",
                               #output="Thesis_LMM_Outputs/Thesis_FMRIP_Agg_ISC.docx",
                               gof_omit = "F|RMSE|Log") %>% dplyr::select(-part, -statistic)

AggBoth_ISC_models
```

# Making Figures

# Individual Choice: Affective ratings and choice ratings.
```{r}

Individual_BothTrailers_df

PA_W_Both_Ind_fig <- ggplot(filter(Individual_BothTrailers_df, Type=="Comedy" | Type=="Horror")
                            , aes(x = (Pos_arousal_scaled), y = (W_score))) +
  labs(x="Positive Arousal", y="Watch Choice") +
  geom_point(aes(color=Type,)) +  
  geom_smooth(method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) +
  stat_cor() +
  ylim(1, 4)

  #geom_text(aes(label = Trailer, color=Type), vjust = 2, show_guide=FALSE) 
  #theme(legend.position="none")

NA_W_Both_Ind_fig <- ggplot(filter(Individual_BothTrailers_df, Type=="Comedy" | Type=="Horror")
                            , aes(x = (Neg_arousal_scaled), y = (W_score))) +
  labs(x="Negative Arousal", y="Watch Choice") +
  geom_point(aes(color=Type,)) +  
  geom_smooth(method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) +
  stat_cor() +
  ylim(1, 4)

PA_W_Separate_Ind_fig <- ggplot(filter(Individual_BothTrailers_df, Type=="Comedy" | Type=="Horror")
                            , aes(x = (Pos_arousal_scaled), y = (W_score), color=Type)) +
  labs(x="Positive Arousal", y="Watch Choice") +
  geom_point(aes(color=Type,)) +  
  geom_smooth(aes(group=Type), method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) +
  stat_cor(show.legend = FALSE) +
  ylim(1, 4)

NA_W_Separate_Ind_fig <- ggplot(filter(Individual_BothTrailers_df, Type=="Comedy" | Type=="Horror")
                            , aes(x = (Neg_arousal_scaled), y = (W_score), color=Type)) +
  labs(x="Negative Arousal", y="Watch Choice") +
  geom_point(aes(color=Type,)) +  
  geom_smooth(aes(group=Type), method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) +
  stat_cor(show.legend = FALSE) +
  ylim(1, 4)

# Arrange and save PA_W and NA_W Both.
AffectiveRatings_WScore_Ind_fig <- ggarrange(
  PA_W_Both_Ind_fig,
  NA_W_Both_Ind_fig+ylab(NULL),
  labels = c("A", "B"),
  nrow = 1,
  align = 'v',
  legend="right",
  common.legend=TRUE,
  widths = 1,
  heights = 1
)

ggsave(
  "AffectiveRatings_WScore_Ind_fig.png",
  plot = AffectiveRatings_WScore_Ind_fig,
  scale = 1,
  width = 9,
  height = 4.5)

AffectiveRatings_WScore_Ind_fig
```

# Individual Choice: Compute partial correlations for NAcc peak (NAcc_IP).
```{r}
# Select specified cols specified cols.
# Decide whether of not to remove peaks with values less than zero.
Individual_ComedyTrailers_rm_nans_df <- dplyr::select(Individual_BothTrailers_df, NAcc_ind_peaks_pos, AIns_ind_peaks_pos, MPFC_ind_peaks_pos, W_score, Type, Participant, Trailer) %>%
  filter(Type=="Comedy")#, W_score >0, NAcc_ind_peaks_pos>0, AIns_ind_peaks_pos>0, MPFC_ind_peaks_pos>0)

Individual_HorrorTrailers_rm_nans_df <- dplyr::select(Individual_BothTrailers_df, NAcc_ind_peaks_pos, AIns_ind_peaks_pos, MPFC_ind_peaks_pos, W_score, Type, Participant, Trailer) %>%
  filter(Type=="Horror")#, W_score >0, NAcc_ind_peaks_pos>0, AIns_ind_peaks_pos>0, MPFC_ind_peaks_pos>0)


# Remove nan's from dataframes.  
Individual_ComedyTrailers_rm_nans_df <- na.omit(Individual_ComedyTrailers_rm_nans_df)
Individual_HorrorTrailers_rm_nans_df <- na.omit(Individual_HorrorTrailers_rm_nans_df)

#Individual_ComedyTrailers_rm_nans_df <- filter(Individual_BothTrailers_df, Type=="Comedy")
#Individual_HorrorTrailers_rm_nans_df <- filter(Individual_BothTrailers_df, Type=="Horror")

# Obtain residuals for Comedy df.
NAcc_Comedy_residuals <- residuals(lmer(NAcc_ind_peaks_pos ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_ComedyTrailers_rm_nans_df) )

AIns_Comedy_residuals <- residuals(lmer(AIns_ind_peaks_pos ~ 

                        (1|Participant) + (1|Trailer), , 
                      data = Individual_ComedyTrailers_rm_nans_df) )

W_Comedy_residuals <- residuals(lmer(W_score ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_ComedyTrailers_rm_nans_df) )

#Obtains residuals from Horror df. 
NAcc_Horror_residuals <- residuals(lmer(NAcc_ind_peaks_pos ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_HorrorTrailers_rm_nans_df) )

AIns_Horror_residuals <- residuals(lmer(AIns_ind_peaks_pos ~ 

                        (1|Participant) + (1|Trailer), , 
                      data = Individual_HorrorTrailers_rm_nans_df) )

W_Horror_residuals <- residuals(lmer(W_score ~ 
                        (1|Participant) + (1|Trailer), #(1|Participant) + (1|Trailer), 
                      data = Individual_HorrorTrailers_rm_nans_df) )


# Create a data frame with residuals
Comedy_residuals_data <- data.frame("NAcc_residuals"=NAcc_Comedy_residuals, 
                                    "W_residuals"=W_Comedy_residuals)
Comedy_residuals_data$Type = "Comedy"
Horror_residuals_data <- data.frame("NAcc_residuals"=NAcc_Horror_residuals, 
                                    "W_residuals"=W_Horror_residuals)
Horror_residuals_data$Type = "Horror"

# Merge dataframes. 
Both_residuals_data <- rbind(Comedy_residuals_data, Horror_residuals_data)

# Plot partial correlation using ggplot2
Ind_BothT_NAccIP_WScore_PartialCor_fig <- ggplot(Both_residuals_data, aes(x = NAcc_residuals, y = W_residuals)) +
  geom_point(aes(color=Type)) +
  geom_smooth( method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) +
  xlab("NAcc_IP ~ (1|Participant) + (1|Trailer)") +
  ylab("W_score ~ (1|Participant) + (1|Trailer)") +
  stat_cor() 

Ind_SepT_NAccIP_WScore_PartialCor_fig <- ggplot(Both_residuals_data, aes(x = NAcc_residuals, y = W_residuals, color=Type)) +
  xlab("NAcc_IP ~ (1|Participant) + (1|Trailer)") +
  ylab("W_score ~ (1|Participant) + (1|Trailer)") +
  geom_point(aes(color=Type)) +
  geom_smooth(aes(group=Type), method="lm", color="black") + #+
  stat_cor(show.legend=FALSE) +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) 

# Arrange and save plots.
NAccIP_WScore_fig <- ggarrange(
  Ind_BothT_NAccIP_WScore_PartialCor_fig,
  Ind_SepT_NAccIP_WScore_PartialCor_fig+ylab(NULL),
  labels = c("A", "B"),
  nrow = 1,
  align = 'v',
  legend="right",
  common.legend=TRUE,
  widths = 1,
  heights = 1
)

ggsave(
  "NAccIP_WScore_Ind_fig.png",
  plot = NAccIP_WScore_fig,
  scale = 1,
  width = 9,
  height = 4.5)

NAccIP_WScore_fig
```

# Individual Choice: Compute partial correlations for AIns modal peak (AIns_MP).
```{r}
Individual_ComedyTrailers_df <- filter(Individual_BothTrailers_df, Type=="Comedy", W_score >0, !is.na(AIns_DP2))
Individual_HorrorTrailers_df <- filter(Individual_BothTrailers_df, Type=="Horror", W_score >0, !is.na(AIns_DP2))

# Obtain AIns Comedy residuals.
AInsMP_Comedy_residuals <- residuals(lmer(AIns_DP2 ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_ComedyTrailers_df) )

W_Comedy_residuals <- residuals(lmer(W_score ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_ComedyTrailers_df) )

# Obtain AIns Horror residuals. 
AInsMP_Horror_residuals <- residuals(lmer(AIns_DP2 ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_HorrorTrailers_df) )

W_Horror_residuals <- residuals(lmer(W_score ~ 
                        (1|Participant) + (1|Trailer), , 
                      data = Individual_HorrorTrailers_df) )

# Create a data frame with residuals
Comedy_residuals_data <- data.frame("AInsMP_residuals"=AInsMP_Comedy_residuals, 
                                    "W_residuals"=W_Comedy_residuals)
Comedy_residuals_data$Type = "Comedy"
Horror_residuals_data <- data.frame("AInsMP_residuals"=AInsMP_Horror_residuals, 
                                    "W_residuals"=W_Horror_residuals)
Horror_residuals_data$Type = "Horror"

# Merge dataframes. 
Both_residuals_AInsMP_data <- rbind(Comedy_residuals_data, Horror_residuals_data)

# Plot partial correlation using ggplot2
Ind_BothT_AInsMP_WScore_PartialCor_fig <- ggplot(Both_residuals_AInsMP_data, aes(x = AInsMP_residuals, y = W_residuals)) +
  geom_point(aes(color=Type)) +
  geom_smooth( method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) +
  xlab("AIns MP ~ (1|Participant) + (1|Trailer)") +
  ylab("W_score ~ (1|Participant) + (1|Trailer)") +
  stat_cor() 

Ind_SepT_AInsMP_WScore_PartialCor_fig <- ggplot(Both_residuals_AInsMP_data, aes(x=AInsMP_residuals, y = W_residuals, color=Type)) +
  xlab("AIns MP ~ (1|Participant) + (1|Trailer)") +
  ylab("W_score ~ (1|Participant) + (1|Trailer)") +
  geom_point(aes(color=Type)) +
  geom_smooth(aes(group=Type), method="lm", color="black") + #+
  stat_cor(show.legend=FALSE) +
  scale_color_manual(name="Genre", labels=c('Comedy', 'Horror'), values = c("Comedy" = "blue", "Horror" = "red")) 

# Arrange and save plots.
AIndMP_WScore_fig <- ggarrange(
  Ind_BothT_AInsMP_WScore_PartialCor_fig,
  Ind_SepT_AInsMP_WScore_PartialCor_fig+ylab(NULL),
  labels = c("A", "B"),
  nrow = 1,
  align = 'v',
  legend="right",
  common.legend=TRUE,
  widths = 1,
  heights = 1
)

ggsave(
  "AInsMP_WScore_Ind_fig.png",
  plot = AIndMP_WScore_fig,
  scale = 1,
  width = 9,
  height = 4.5)

AIndMP_WScore_fig
```


# Aggregate Choice: NAcc Modal peak & First Month Box Office
```{r}
NAcc_MP_Both_Agg_fig <- ggplot(Aggregate_BothTrailers_df, aes(x = (NAcc_DP2), y = log(Gross_M1_updated))) +
  labs(x="NAcc Modal Peak", y="First Moth Gross (Log)") +
  geom_point(aes(color=Type,)) +  
  geom_smooth(method = "lm", fill="gray", colour="black") +
  scale_color_manual(name="Genre", labels=c('Horror', 'Comedy'), values = c("comedy" = "blue", "horror" = "red")) +
  stat_cor() #+
  #geom_text(aes(label = Trailer, color=Type), vjust = 2, show_guide=FALSE) 
  #theme(legend.position="none")


NAcc_MP_Both_Agg_fig + theme(legend.position="none")

```
# Aggregate Choice: NAcc Modal peak & First Month Box Office By Genre
```{r}
Aggregate_ComedyTrailers_df <- filter(Aggregate_BothTrailers_df, Type=="comedy")

NAcc_MP_BothSep_Agg_fig <- ggplot(Aggregate_BothTrailers_df, aes(x = (NAcc_DP2), y = log(Gross_M1_updated), color=Type)) +
  labs(x="NAcc Modal Peak", y="First Moth Gross (Log)") +
  geom_point(aes(color=Type),) +  
  geom_smooth(aes(group=Type), method="lm", color="black") +
  scale_color_manual(name="Genre", labels=c('Horror', 'Comedy'), values=c("comedy"="blue", "horror"= "red")) +
  stat_cor(show.legend=FALSE) #+
  #geom_text(aes(label = Trailer, color=Type), vjust = 2, show_guide=FALSE) 
  #theme_cowplot(12)
NAcc_MP_BothSep_Agg_fig

# Get scaled of figure. 
#layer_scales(NAcc_MP_BothSep_Agg_fig)$y$range$range

```

```{r}

# Define the individual plots
plot1 <- ggplot(Aggregate_BothTrailers_df, aes(x = NAcc_DP2, y = log(Gross_M1_updated))) +
  labs(x = "NAcc Modal Peak", y = "First Month Gross (Log)") +
  geom_point(aes(color = Type)) +  
  geom_smooth(method = "lm", fill = "gray", colour = "black") +
  scale_color_manual(name = "Genre", labels = c('Horror', 'Comedy'), values = c("comedy" = "blue", "horror" = "red")) +
  stat_cor() +
  #geom_text(aes(label = Trailer, color = Type), vjust = 2, show.legend = FALSE) +
  ylim(15.09155, 19.255) +
  theme(legend.position = "none")

plot2 <- ggplot(Aggregate_BothTrailers_df, aes(x = NAcc_DP2, y = log(Gross_M1_updated), color = Type)) +
  labs(x = "NAcc Modal Peak", y = "First Month Gross (Log)") +
  geom_point(aes(color = Type)) +  
  geom_smooth(aes(group = Type), method = "lm", color = "black") +
  scale_color_manual(name = "Genre", labels = c('Horror', 'Comedy'), values = c("comedy" = "blue", "horror" = "red")) +
  stat_cor(show.legend = FALSE) +
  #geom_text(aes(label = Trailer, color = Type), vjust = 2, show.legend = FALSE) + 
  ylim(15.09155, 19.255) +
  ylab(NULL)  

# Combine the plots
prow <- ggarrange(
  plot1,
  plot2,
  labels = c("A", "B"),
  nrow = 1,
  align = 'v',
  legend="right",
  common.legend=TRUE,
  widths = 1,
  heights = 1
)

print(prow)
ggsave(
  "NAcc_ModalPeal_Aggregate.png",
  plot = prow,
  scale = 1,
  width = 9,
  height = 4.5)

```
```{r}
prow <- plot_grid(
  ggplot(Aggregate_BothTrailers_df, aes(x = NAcc_DP2, y = log(Gross_M1_updated))) +
    labs(x="NAcc Modal Peak", y="First Month Gross (Log)") +
    geom_point(aes(color=Type)) +  
    geom_smooth(method = "lm", fill="gray", colour="black") +
    scale_color_manual(name="Genre", labels=c('Horror', 'Comedy'), values=c("comedy" = "blue", "horror" = "red")) +
    stat_cor() +
    geom_text(aes(label = Trailer, color=Type), vjust = 2, show.legend=FALSE) +
    theme(legend.position="none"),
  
  ggplot(Aggregate_BothTrailers_df, aes(x = NAcc_DP2, y = log(Gross_M1_updated), color=Type)) +
    labs(x="NAcc Modal Peak", y="First Month Gross (Log)") +
    geom_point(aes(color=Type)) +  
    geom_smooth(aes(group=Type), method="lm", color="black") +
    scale_color_manual(name="Genre", labels=c('Horror', 'Comedy'), values=c("comedy"="blue", "horror"="red")) +
    stat_cor(show.legend=FALSE) +
    geom_text(aes(label = Trailer, color=Type), vjust = 2, show.legend=FALSE) + 
    ylab(NULL) + 
    theme(legend.position="none"),
  
  align = 'vh',
  labels = c("A", "B"),
  hjust = -1,
  nrow = 1
)

print(prow)
```




# Make Task and ROIs figures.
```{r,  echo=FALSE}


NAcc_mask_fig <- ggdraw() +
  draw_image("Figures/Thesis/NAccMask_Fig.png", scale = 1) 
  

AIns_mask_fig <- ggdraw() +
  draw_image("Figures/Thesis/AInsMask_Fig.png", scale = 1)

MPFC_mask_fig <- ggdraw() +
  draw_image("Figures/Thesis/MPFCMask_Fig.png", scale = 1)

Task_fig <- ggdraw() +
  draw_image("Figures/Thesis/MovieTrask_fig.png", scale = 1)

#ggarrange(Task_fig, NAcc_mask_fig, AIns_mask_fig, MPFC_mask_fig,
#          labels = c("A", "B", "C", "D"),
#          ncol = 3, nrow = 2)

Task_ROI_fig <- ggarrange(ggarrange(Task_fig, ncol = 1, labels = c("A")) , 
          ggarrange(NAcc_mask_fig, AIns_mask_fig, MPFC_mask_fig,
          labels = c("B", "C", "D"), ncol = 3),
          labels = c("", ""), 
          nrow = 2) + bgcolor("white") 
         


ggsave(
  "Task_ROI_fig.png",
  plot = Task_ROI_fig,
  scale = 1,
  width = 9,
  height = 4.5)
    
Task_ROI_fig
```






